\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/1782\_in\_science\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{1782 in science}\label{in-science}

\begin{itemize}
\item
  \emph{The year 1782 in science and technology included many events,
  some of which are listed here.}
\end{itemize}

The year 1782 in science and technology included many events, some of
which are listed here.

\section{Aviation}\label{aviation}

\begin{itemize}
\item
  \emph{December 14 -- The Montgolfier brothers first test fly a hot air
  balloon; it floats nearly 2~km (1.2~mi).}
\end{itemize}

December 14 -- The Montgolfier brothers first test fly a hot air
balloon; it floats nearly 2~km (1.2~mi).

\section{Biology}\label{biology}

\begin{itemize}
\item
  \emph{Jesuit abbot Juan Ignacio Molina publishes Saggio sulla Storia
  Naturale del Chili in Spain, the first account of the natural history
  of his native Chile, describing many species to science for the first
  time (e.g., Araucaria araucana).}
\end{itemize}

Jesuit abbot Juan Ignacio Molina publishes Saggio sulla Storia Naturale
del Chili in Spain, the first account of the natural history of his
native Chile, describing many species to science for the first time
(e.g., Araucaria araucana).

\section{Chemistry}\label{chemistry}

\begin{itemize}
\item
  \emph{Winter 1782--83 -- Antoine Lavoisier and Pierre-Simon Laplace
  begin to use the world's first ice calorimeter to determine the heat
  evolved in various chemical changes (calculations based on Joseph
  Black's prior discovery of latent heat), marking the foundation of
  thermochemistry.}
\end{itemize}

Winter 1782--83 -- Antoine Lavoisier and Pierre-Simon Laplace begin to
use the world's first ice calorimeter to determine the heat evolved in
various chemical changes (calculations based on Joseph Black's prior
discovery of latent heat), marking the foundation of thermochemistry.

\section{Technology}\label{technology}

\begin{itemize}
\item
  \emph{John Arnold patents his improvements in the construction of
  marine chronometers in Britain.}
\end{itemize}

John Arnold patents his improvements in the construction of marine
chronometers in Britain.

\section{Physics}\label{physics}

\begin{itemize}
\item
  \emph{Giordano Riccati publishes experiments determining what will
  later be known as Young's modulus.}
\item
  \emph{Jean-Paul Marat publishes Recherches physiques sur l'électricité
  (Research into the Physics of Electricity)}
\end{itemize}

Jean-Paul Marat publishes Recherches physiques sur l'électricité
(Research into the Physics of Electricity)

Giordano Riccati publishes experiments determining what will later be
known as Young's modulus.

\section{Institutions}\label{institutions}

\begin{itemize}
\item
  \emph{Princess Yekaterina Vorontsova-Dashkova is appointed Director of
  the Imperial Academy of Arts and Sciences in Saint Petersburg.}
\end{itemize}

Princess Yekaterina Vorontsova-Dashkova is appointed Director of the
Imperial Academy of Arts and Sciences in Saint Petersburg.

\section{Awards}\label{awards}

\begin{itemize}
\item
  \emph{Copley Medal: Richard Kirwan}
\end{itemize}

Copley Medal: Richard Kirwan

\section{Births}\label{births}

\begin{itemize}
\item
  \emph{June 16 -- Olry Terquem, French Jewish geometer (died 1862)}
\item
  \emph{June 3 -- Charles Waterton, English naturalist and explorer
  (died 1865)}
\item
  \emph{April 7 -- Marie-Anne Libert, Belgian botanist (died 1865)}
\end{itemize}

April 7 -- Marie-Anne Libert, Belgian botanist (died 1865)

June 3 -- Charles Waterton, English naturalist and explorer (died 1865)

June 16 -- Olry Terquem, French Jewish geometer (died 1862)

\section{Deaths}\label{deaths}

\begin{itemize}
\item
  \emph{May 16 -- Daniel Solander, Swedish-born botanist (born 1733)}
\item
  \emph{Elisabeth Christina von Linné, Swedish botanist (born 1743)}
\item
  \emph{January 18 -- Sir John Pringle, Scottish-born physician (born
  1707)}
\item
  \emph{May 20 -- William Emerson, English mathematician (born 1701)}
\item
  \emph{March 17 -- Daniel Bernoulli, Dutch-Swiss mathematician (born
  1700)}
\end{itemize}

January 18 -- Sir John Pringle, Scottish-born physician (born 1707)

March 17 -- Daniel Bernoulli, Dutch-Swiss mathematician (born 1700)

May 16 -- Daniel Solander, Swedish-born botanist (born 1733)

May 20 -- William Emerson, English mathematician (born 1701)

Elisabeth Christina von Linné, Swedish botanist (born 1743)

unknown date -- Christine Kirch, German astronomer (born 1696)

\section{References}\label{references}
