\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Air\%20Force\%20Life\%20Cycle\%20Management\%20Center\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Air Force Life Cycle Management
Center}\label{air-force-life-cycle-management-center}

\begin{itemize}
\item
  \emph{Led by a Lieutenant General, AFLCMC is charged with life cycle
  management of Air Force weapon systems from their inception to
  retirement.}
\item
  \emph{The Air Force Life Cycle Management Center (AFLCMC),
  headquartered at Wright-Patterson AFB, is one of six centers reporting
  to the Air Force Materiel Command.}
\end{itemize}

The Air Force Life Cycle Management Center (AFLCMC), headquartered at
Wright-Patterson AFB, is one of six centers reporting to the Air Force
Materiel Command.\\
Led by a Lieutenant General, AFLCMC is charged with life cycle
management of Air Force weapon systems from their inception to
retirement. The AFLCMC mission is to acquire and support war-winning
capabilities.

AFLCMC was designed to provide a single face and voice to customers,
holistic management of weapon systems across their life cycles, and to
simplify and consolidate staff functions and processes to curtail
redundancy and enhance efficiency. In addition AFLCMC's operating
structure provides an integrated framework for decision making and
process optimization across the weapon system life cycle. AFLCMC
personnel work closely with their counterparts at the other four AFMC
centers.

\section{Organization}\label{organization}

\begin{itemize}
\item
  \emph{The Air Force Security Assistance and Cooperation Directorate
  oversees execution of the foreign military sales mission.}
\item
  \emph{Each Program Office reports to one of 10 Program Executive
  Officers (PEOs) who are accountable for the activities within their
  portfolio and who report to the Air Force Service Acquisition
  Executive at the Pentagon (Assistant Secretary of the Air Force for
  Acquisition).}
\item
  \emph{The 66th Air Base Group at Hanscom AFB, Mass., and the 88th Air
  Base Wing at Wright-Patterson AFB provide base operating support at
  those locations and also report to AFLCMC.}
\end{itemize}

AFLCMC's portfolio includes: Information Technology systems and
networks; Command, Control, Communications, Intelligence, Surveillance
and Reconnaissance systems (C3I and Networks AFPEO at Hanscom AFB;
Armament Directorate at Eglin Air Force Base, FL; strategic systems;
aerial platforms; and various specialized or supporting systems such as
simulators or personal equipment. AFLCMC also executes sales of aircraft
and other defense-related equipment while building security assistance
relationships with foreign partner nation air forces. Approximately
26,000 AFLCMC airmen, civilian and contractor employees perform center
missions from some 75 locations.

Each Program Office reports to one of 10 Program Executive Officers
(PEOs) who are accountable for the activities within their portfolio and
who report to the Air Force Service Acquisition Executive at the
Pentagon (Assistant Secretary of the Air Force for Acquisition).

AFLCMC execution directorates provide direct program support such as
engineering, technical order management, developmental planning,
contracting, and source selection assistance. The execution directorates
include: Technical Engineering Services; Intelligence; Cost and
Financial Analysis; Program Development \& Integration; Contracting
Execution; and Life Cycle Management and Services. The Air Force
Security Assistance and Cooperation Directorate oversees execution of
the foreign military sales mission. The Airborne Laser Directorate
executes a technology development mission for high altitude,
anti-ballistic missile, directed energy capabilities and reports to the
Missile Defense Agency. A Propulsion Directorate headquartered at Tinker
AFB, Okla., oversees engine acquisition executed at Wright-Patterson and
engine product support accomplished at Tinker.

The 66th Air Base Group at Hanscom AFB, Mass., and the 88th Air Base
Wing at Wright-Patterson AFB provide base operating support at those
locations and also report to AFLCMC.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Air Force Materiel Command Units (official)}
\item
  \emph{Air Force Life Cycle Management Center Homepage (official)}
\end{itemize}

Air Force Life Cycle Management Center Homepage (official)

Air Force Materiel Command Units (official)
