\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Anthony\_Quartuccio\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Anthony Quartuccio}\label{anthony-quartuccio}

\begin{itemize}
\item
  \emph{Anthony Quartuccio is an American music director and conductor.}
\end{itemize}

Anthony Quartuccio is an American music director and conductor.

\section{Career}\label{career}

\begin{itemize}
\item
  \emph{Quartuccio received a Bachelor of Music Degree from Santa Clara
  University.}
\item
  \emph{Quartuccio has conducted both concert halls and Operas.}
\end{itemize}

Quartuccio has conducted both concert halls and Operas. He has made
appearances around the country and in Asia and the Czech Republic.
Quartuccio received a Bachelor of Music Degree from Santa Clara
University. In 2006 he received a lifetime achievement award in the Arts
from the Italian American Heritage Foundation.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{Quartuccio's father, Anthony Quartuccio, Sr. (November 1922 -
  October 16, 2011) was a locally renowned author and illustrator in
  Northern California.}
\end{itemize}

Quartuccio's father, Anthony Quartuccio, Sr. (November 1922 - October
16, 2011) was a locally renowned author and illustrator in Northern
California.

\section{References}\label{references}

\section{External links}\label{external-links}
