\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Bentot\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Bentot}\label{bentot}

\begin{itemize}
\item
  \emph{Norvin Guerrero (1928 - 1986), better known by his stage name
  Bentot or Ben Cosca, was a Filipino comedian and vaudevillian who
  spent most of his career under LVN Pictures.}
\end{itemize}

Norvin Guerrero (1928 - 1986), better known by his stage name Bentot or
Ben Cosca, was a Filipino comedian and vaudevillian who spent most of
his career under LVN Pictures. He made many box office hits with another
famed comedian Pugo who played as his father in their films. He also
appeared on the Manila bodabil circuit in its heyday in the fifties and
early sixties.

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{Then he moved to the rival studio of Sampaguita, LVN, and stayed
  until the film studio closed in 1961.}
\item
  \emph{He is the father of former child star Bentot Jr.}
\item
  \emph{He made his second and last movie for Sampaguita in 1951's Batas
  ng Daigdig aka Rule of the World.}
\item
  \emph{He made his first movie appearance in 1947's Maria Kapra, a
  musical by Sampaguita Pictures with Angel Esmeralda.}
\end{itemize}

Arturo Vergara Medina was born in San Simon, Pampanga in 1928.

He made his first movie appearance in 1947's Maria Kapra, a musical by
Sampaguita Pictures with Angel Esmeralda. He made his second and last
movie for Sampaguita in 1951's Batas ng Daigdig aka Rule of the World.
Then he moved to the rival studio of Sampaguita, LVN, and stayed until
the film studio closed in 1961.

Bentot had a second life in radio and television, appearing in the radio
and later TV comedy series Tang Tarang Tang with Pugo, Rosa Aguirre and
Marita Zobel.

He is the father of former child star Bentot Jr.

\section{Death}\label{death}

\begin{itemize}
\item
  \emph{Bentot died in 1986 at the age of 58 years, due to heart
  failure.}
\end{itemize}

Bentot died in 1986 at the age of 58 years, due to heart failure.

\section{Filmography}\label{filmography}

\begin{itemize}
\item
  \emph{1957 -Phone Pal {[}LVN{]}}
\item
  \emph{1959 -Nukso ng Nukso {[}LVN{]}}
\item
  \emph{1951 -Batas ng Daigdig {[}Sampaguita{]}}
\item
  \emph{1958 -Mr. Kuripot {[}LVN{]}}
\item
  \emph{1957 -Sebya, Mahal Kita {[}LVN{]}}
\item
  \emph{1958 -Alembong {[}LVN{]}}
\item
  \emph{{[}LVN{]}}
\end{itemize}

1947 -Maria Kapra {[}Sampaguita{]}

1951 -Batas ng Daigdig {[}Sampaguita{]}

1957 -Phone Pal {[}LVN{]}

1957 -Sebya, Mahal Kita {[}LVN{]}

1958 -Alembong {[}LVN{]}

1958 -Mr. Kuripot {[}LVN{]}

1959 -Nukso ng Nukso {[}LVN{]}

1960 -Oh Sendang! {[}LVN{]}

1976 -Taho-Ichi {[}GPS{]}

1985 -The Crazy Professor {[}RVQ{]}(his last movie)

\section{Discography}\label{discography}

\begin{itemize}
\item
  \emph{1978 - Burloloy - Plaka Pilipino Records}
\item
  \emph{1978 - Jeproks - Plaka Pilipino Records}
\end{itemize}

1978 - Jeproks - Plaka Pilipino Records

1978 - Burloloy - Plaka Pilipino Records

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Bentot on IMDb}
\item
  \emph{Bentot film clips}
\end{itemize}

Bentot on IMDb

Bentot film clips
