\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Bret\%20Baier\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Bret Baier}\label{bret-baier}

\begin{itemize}
\item
  \emph{William Bret Baier (born August 4, 1970) is the host of Special
  Report with Bret Baier on the Fox News Channel and serves as the chief
  political anchor for Fox.}
\end{itemize}

William Bret Baier (born August 4, 1970) is the host of Special Report
with Bret Baier on the Fox News Channel and serves as the chief
political anchor for Fox. He previously worked as the network's Chief
White House Correspondent and Pentagon correspondent.

\section{Early life and education}\label{early-life-and-education}

\begin{itemize}
\item
  \emph{Baier was born in Rumson, New Jersey.}
\item
  \emph{Baier then attended DePauw University in Greencastle, Indiana,
  graduating in 1992 with a BA degree in political science and English.}
\end{itemize}

Baier was born in Rumson, New Jersey. Raised Catholic, he attended
Marist High School, a private Roman Catholic high school in Atlanta,
Georgia, graduating in 1988. Baier then attended DePauw University in
Greencastle, Indiana, graduating in 1992 with a BA degree in political
science and English. At DePauw, he became a member of the Xi Chapter of
the Sigma Chi Fraternity.

\section{Career}\label{career}

\begin{itemize}
\item
  \emph{Psaki, who sent the email, later apologized to Baier.}
\item
  \emph{On December 23, 2008, Brit Hume anchored his final show and
  announced Baier would replace him as anchor of Special Report.}
\item
  \emph{He was named Fox News's White House correspondent in 2007,
  covering the administration of George W. Bush.}
\item
  \emph{He hosted his first show as permanent anchor on January 5,
  2009.}
\end{itemize}

Baier began his television career with a local station in Rockford,
Illinois, before joining WRAL-TV, then CBS now NBC affiliate (As of
February 29, 2016) in Raleigh, North Carolina. He sent an audition tape
to Fox News in 1998, and was hired as the network's Atlanta bureau
chief. On September 11, 2001, he drove from Georgia to Arlington,
Virginia, to cover the attack on the Pentagon. He never returned to the
Atlanta bureau and was instead tapped as the network's Pentagon
correspondent, remaining at the post for five years and taking 11 trips
to Afghanistan and 13 trips to Iraq.

He was named Fox News's White House correspondent in 2007, covering the
administration of George W. Bush. In the fall of 2007, he began
substituting for Brit Hume, then the anchor of Special Report, on
Fridays.

On December 23, 2008, Brit Hume anchored his final show and announced
Baier would replace him as anchor of Special Report. He hosted his first
show as permanent anchor on January 5, 2009.

A Freedom of Information Act request filed to investigate anti-Fox News
bias in the Barack Obama administration revealed an internal email
written by Deputy White House Communications Director, Jennifer Psaki,
dated October 23, 2009, that referred to Baier as a "lunatic." Psaki,
who sent the email, later apologized to Baier.

\section{Accolades}\label{accolades}

\begin{itemize}
\item
  \emph{2018 Urbino Press Award, Municipality of Urbino}
\item
  \emph{2016 Kenneth Y. Tomlinson Award for Outstanding Journalism,
  Robert Novak Journalism Fellowship Program}
\item
  \emph{2017 Sol Taishoff Award for Excellence in Broadcast Journalism,
  National Press Foundation}
\end{itemize}

2016 Kenneth Y. Tomlinson Award for Outstanding Journalism, Robert Novak
Journalism Fellowship Program

2017 Sol Taishoff Award for Excellence in Broadcast Journalism, National
Press Foundation

2018 Urbino Press Award, Municipality of Urbino

\section{Retracted reporting}\label{retracted-reporting}

\begin{itemize}
\item
  \emph{One day later, on November 4, Baier retracted and apologized for
  both stories, now saying there was no evidence at this time for either
  allegation.}
\item
  \emph{On November 2, 2016, six days before the election, Baier led off
  his news show with a report that multiple FBI sources told him that it
  was 99\% likely that Hillary Clinton's email server had been hacked by
  ``five foreign intelligence agencies.'' The next day, Baier reported
  there would "likely be an indictment" in the investigation of Hillary
  Clinton's role in the Clinton Foundation and State Department.}
\end{itemize}

On November 2, 2016, six days before the election, Baier led off his
news show with a report that multiple FBI sources told him that it was
99\% likely that Hillary Clinton's email server had been hacked by
``five foreign intelligence agencies.'' The next day, Baier reported
there would "likely be an indictment" in the investigation of Hillary
Clinton's role in the Clinton Foundation and State Department. One day
later, on November 4, Baier retracted and apologized for both stories,
now saying there was no evidence at this time for either allegation. No
explanation was given as to how his originally-claimed multiple
informants had all given him the same unverified story.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{In 2009, Baier was named a "Significant Sig" by the Sigma Chi
  Fraternity.}
\item
  \emph{Baier and his wife Amy have two sons, Daniel and Paul.}
\item
  \emph{On January 21, 2019, Baier and his family were involved in an
  automobile accident in Montana, where the family was on a skiing
  weekend.}
\item
  \emph{Baier, who served as an altar boy in his youth, is a practicing
  Roman Catholic and attends Holy Trinity Catholic Church in
  Georgetown.}
\end{itemize}

Baier, who served as an altar boy in his youth, is a practicing Roman
Catholic and attends Holy Trinity Catholic Church in Georgetown.

Baier and his wife Amy have two sons, Daniel and Paul. One of their sons
was born with cardiac problems and before the child's open-heart surgery
in 2008, President George W. Bush invited Baier and his wife and son to
the Oval Office for a visit and had the White House physician update him
on Paul's progress. In 2009, Baier was named a "Significant Sig" by the
Sigma Chi Fraternity.

On January 21, 2019, Baier and his family were involved in an automobile
accident in Montana, where the family was on a skiing weekend.

\section{See also}\label{see-also}

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{FOX News Channel: Bret Baier bio}
\end{itemize}

FOX News Channel: Bret Baier bio

Appearances on C-SPAN
