\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Clathrina\_mutsu\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Clathrina mutsu}\label{clathrina-mutsu}

\begin{itemize}
\item
  \emph{The species is named after the type locality, Mutsu Bay}
\item
  \emph{Clathrina mutsu is a species of calcareous sponge from Japan.}
\end{itemize}

Clathrina mutsu is a species of calcareous sponge from Japan. The
species is named after the type locality, Mutsu Bay

\section{Description}\label{description}

\begin{itemize}
\item
  \emph{The skeleton is composed of triradiates arranged in a few
  confused layers in the walls of ascon-tubes.}
\item
  \emph{The sponge forms irregular, spreading masses consisting of a
  loose network of ascon-tubes with varying closeness of its meshes in
  different specimens and in different parts of the same colony.}
\item
  \emph{The sponge is rather small and attains the length of 0.5 --
  12~mm.}
\end{itemize}

The sponge forms irregular, spreading masses consisting of a loose
network of ascon-tubes with varying closeness of its meshes in different
specimens and in different parts of the same colony. The oscula are
found as small round apertures distributed here and there on the surface
of the ascon-tubes. The sponge is rather small and attains the length of
0.5 -- 12~mm. The diameter of ascon-tubes varies a good deal in
different parts of the same colony, measuring about 0.15 - 0.6~mm. The
colour of the sponge is brownish-white when preserved in alcohol. The
skeleton is composed of triradiates arranged in a few confused layers in
the walls of ascon-tubes. In addition to the triradiates, a few
quadriradiates can occasionally be found. The triradiates are regular
with straight, conical, and gradually sharp-pointed rays, measuring 60 -
150 μm in length and 8 - 14 μm thick at the base.

\section{References}\label{references}

\begin{itemize}
\item
  \emph{World Register of Marine Species entry}
\end{itemize}

World Register of Marine Species entry
