\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Cristina\%20Alesci\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Cristina Alesci}\label{cristina-alesci}

\begin{itemize}
\item
  \emph{Cristina Alesci is a CNN and CNNMoney correspondent based out of
  the network's New York bureau.}
\end{itemize}

Cristina Alesci is a CNN and CNNMoney correspondent based out of the
network's New York bureau. She covers breaking news for the network as
well as financial fraud and controversies facing major companies. Her
investigative series focuses on public policy issues of the 2016
election cycle, food production, and documenting the early struggles of
successful leaders.

\section{Early life and education}\label{early-life-and-education}

\begin{itemize}
\item
  \emph{In 2008, Alesci graduated with a M.A.}
\item
  \emph{in Journalism with honors from City University of New York's
  Graduate School of Journalism.}
\end{itemize}

In 2008, Alesci graduated with a M.A. in Journalism with honors from
City University of New York's Graduate School of Journalism. While at
the school, she broke a story that gained national recognition. Her
reporting uncovered an FBI file on journalist David Halberstam in the
mid-1960s. The story was followed by the Associated Press, Politico and
the Huffington Post. Before getting her masters, she graduated magna cum
laude from Pace University in New York City, earning a B.S. in Criminal
Justice. Additionally, she received a post-baccalaureate certificate in
business from Columbia University.

\section{Career}\label{career}

\begin{itemize}
\item
  \emph{After freelancing for several local New York City publications
  and an internship at the New York Daily News, Alesci started as a
  reporter for Bloomberg News where she covered mergers and
  acquisitions, private equity and venture capital.}
\end{itemize}

After freelancing for several local New York City publications and an
internship at the New York Daily News, Alesci started as a reporter for
Bloomberg News where she covered mergers and acquisitions, private
equity and venture capital. She broke news on the biggest deals of the
decade, including Facebook's initial public offering and Dell's takeover
battle. She later transitioned to Bloomberg Television.

\section{CNN}\label{cnn}

\begin{itemize}
\item
  \emph{In 2014, Alesci joined CNN where she frequently appears on the
  network's Newsroom programs, CNN International, and HLN.}
\end{itemize}

In 2014, Alesci joined CNN where she frequently appears on the network's
Newsroom programs, CNN International, and HLN. She also writes for its
websites. In her role as a business reporter, Alesci has interviewed
leading CEOs, including Starbucks' CEO Howard Schultz, JP Morgan chief
executive Jamie Dimon and J.Crew's Mickey Drexler.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{In 2016, Alesci was diagnosed with adult onset Type 1 diabetes.}
\end{itemize}

In 2016, Alesci was diagnosed with adult onset Type 1 diabetes.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{New Yorkers in journalism}
\end{itemize}

New Yorkers in journalism

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Cristina Alesci on Twitter}
\item
  \emph{CNN Profile}
\end{itemize}

CNN Profile

Cristina Alesci on Twitter
