\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/David\%20Garrow\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{David Garrow}\label{david-garrow}

\begin{itemize}
\item
  \emph{David Jeffries Garrow (born May 11, 1953) is an American
  historian and author.}
\item
  \emph{He also wrote Liberty and Sexuality (1994), a history of the
  legal struggles over abortion and reproductive rights in the U.S.
  prior to the Roe v. Wade decision, Rising Star: The Making of Barack
  Obama (2017), and other works.}
\end{itemize}

David Jeffries Garrow (born May 11, 1953) is an American historian and
author. He wrote the book Bearing the Cross: Martin Luther King, Jr.,
and the Southern Christian Leadership Conference (1986), which won the
1987 Pulitzer Prize for Biography. He also wrote Liberty and Sexuality
(1994), a history of the legal struggles over abortion and reproductive
rights in the U.S. prior to the Roe v. Wade decision, Rising Star: The
Making of Barack Obama (2017), and other works.

\section{Life and career}\label{life-and-career}

\begin{itemize}
\item
  \emph{Garrow served as a senior adviser for Eyes on the Prize, the
  award-winning PBS television history of the Civil Rights Movement
  covering the years 1954--1965.}
\item
  \emph{Garrow writes frequently on the history of the United States
  Supreme Court and the history of the Civil Rights Movement, and
  regularly contributes articles on these subjects to non-academic
  publications including The New York Times, The Nation, The Financial
  Times, and The New Republic.}
\end{itemize}

Garrow was born in New Bedford, Massachusetts, the son of Barbara
(Fassett) amd Walter Garrow. He graduated magna cum laude from Wesleyan
University in 1975 before receiving his Ph.D. from Duke University in
1981.

Garrow writes frequently on the history of the United States Supreme
Court and the history of the Civil Rights Movement, and regularly
contributes articles on these subjects to non-academic publications
including The New York Times, The Nation, The Financial Times, and The
New Republic.

Garrow served as a senior adviser for Eyes on the Prize, the
award-winning PBS television history of the Civil Rights Movement
covering the years 1954--1965. He has taught at Duke University
(Instructor of History; 1978--1979), the University of North Carolina at
Chapel Hill (Assistant Professor of History; 1980--1984), the City
College of New York and the CUNY Graduate Center (Associate and full
Professor of History; 1984--1991), The Cooper Union (Visiting
Distinguished Professor of History; 1992--1993), the College of William
and Mary (James Pinckney Harrison Visiting Professor of History;
1994--1995), American University (Distinguished Historian in Residence;
1995--1996) and the Emory University School of Law (Presidential
Distinguished Professor; 1997--2005). From 2005 to 2011, Garrow was a
senior research fellow at Homerton College, Cambridge. From 2011 until
2018 he served as Professor of Law and History and John E. Murray
Faculty Scholar at the University of Pittsburgh School of Law.

Garrow is also a member of the Democratic Socialists of America.

\section{Selected works}\label{selected-works}

\begin{itemize}
\item
  \emph{Bearing the Cross: Martin Luther King, Jr., and the Southern
  Christian Leadership Conference (Morrow, 1986; HarperCollins
  paperback, 2004)}
\item
  \emph{The FBI and Martin Luther King, Jr. (Norton, 1981)}
\item
  \emph{Liberty and Sexuality: The Right to Privacy and the Making of
  Roe v. Wade (Macmillan, 1994; updated paperback edition, University of
  California Press, 1998)}
\end{itemize}

Protest at Selma (Yale University Press, 1978)

The FBI and Martin Luther King, Jr. (Norton, 1981)

Bearing the Cross: Martin Luther King, Jr., and the Southern Christian
Leadership Conference (Morrow, 1986; HarperCollins paperback, 2004)

We Shall Overcome (as editor, three volumes of an 18-volume set, Carlson
Pub., 1989)

Liberty and Sexuality: The Right to Privacy and the Making of Roe v.
Wade (Macmillan, 1994; updated paperback edition, University of
California Press, 1998)

Rising Star: The Making of Barack Obama (2017)

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{David Garrow at the University of Pittsburgh}
\end{itemize}

Appearances on C-SPAN

David Garrow at the University of Pittsburgh
