\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Department\%20of\%20Aerospace\%20Science\%20and\%20Technology\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Department of Aerospace Science and
Technology}\label{department-of-aerospace-science-and-technology}

\begin{itemize}
\item
  \emph{It is subordinated to the Brazilian Air Force (FAB).}
\item
  \emph{The Brazilian Department of Science and Aerospace Technology
  (Portuguese: Departamento de Ciência e Tecnologia Aeroespacial; DCTA)
  is the national military research center for aviation and space
  flight.}
\end{itemize}

The Brazilian Department of Science and Aerospace Technology
(Portuguese: Departamento de Ciência e Tecnologia Aeroespacial; DCTA) is
the national military research center for aviation and space flight. It
is subordinated to the Brazilian Air Force (FAB).

It coordinates all technical and scientific activities related to the
aerospace sector in which there are interests by the Ministry of
Defence. It was established in 1953. It currently employs several
thousand civilian and military personnel.

\section{Institutes}\label{institutes}

\begin{itemize}
\item
  \emph{The DCTA has four institutes within its campus.}
\end{itemize}

The DCTA has four institutes within its campus.

\section{Aeronautics and Space Institute
(IAE)}\label{aeronautics-and-space-institute-iae}

\begin{itemize}
\item
  \emph{In Portuguese, Instituto de Aeronaútica e Espaço.}
\item
  \emph{It develops projects in the aeronautical, airspace and defense
  sectors, co-responsible for the execution of the Brazilian Space
  Mission.}
\end{itemize}

In Portuguese, Instituto de Aeronaútica e Espaço. It develops projects
in the aeronautical, airspace and defense sectors, co-responsible for
the execution of the Brazilian Space Mission.

\section{Aeronautics Institute of Technology
(ITA)}\label{aeronautics-institute-of-technology-ita}

\begin{itemize}
\item
  \emph{It is one of the main educational colleges of the Brazilian Air
  Force.}
\item
  \emph{In Portuguese, Instituto Tecnológico de Aeronáutica.}
\end{itemize}

In Portuguese, Instituto Tecnológico de Aeronáutica. It is one of the
main educational colleges of the Brazilian Air Force.

\section{Institute for Advanced Studies
(IEAv)}\label{institute-for-advanced-studies-ieav}

\begin{itemize}
\item
  \emph{In Portuguese, Instituto de Estudos Avançados.}
\end{itemize}

In Portuguese, Instituto de Estudos Avançados. Responsible for the
development of pure and applied sciences: photonics, nuclear energy,
applied physics, remote sensor systems and decision support systems. In
2006, the IEAv inaugurated the T3 Hypersonic wind tunnel, the largest in
Latin America.

\section{Industrial Promotion and Coordination Institute
(IFI)}\label{industrial-promotion-and-coordination-institute-ifi}

\begin{itemize}
\item
  \emph{In Portuguese, Instituto de Fomento e Coodernação Industrial.}
\end{itemize}

In Portuguese, Instituto de Fomento e Coodernação Industrial. It
provides military aeronautical certification and aerospace equipment
approval, acting as an interface between the institutes and the
industry. Until 2006, it carried out the civil aircraft certification
activities, today under the National Civil Aviation Agency
responsibilities.

\section{Flight Testing and Research Institute
(IPEV)}\label{flight-testing-and-research-institute-ipev}

\begin{itemize}
\item
  \emph{In Portuguese, Instituto de Pesquisas e Ensaios em Voo.}
\end{itemize}

In Portuguese, Instituto de Pesquisas e Ensaios em Voo. This institute
is responsible for the instruction and fulfillment of flight testing
campaigns (founded 1953)\\
.

\section{Museum}\label{museum}

\begin{itemize}
\item
  \emph{The DCTA is also responsible managing for the Brazilian
  Aerospace Memorial (Memorial Aerospacial Brasileiro - MAB).}
\end{itemize}

The DCTA is also responsible managing for the Brazilian Aerospace
Memorial (Memorial Aerospacial Brasileiro - MAB). It is located in São
José dos Campos, São Paulo, Brazil.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Brazilian Space Agency}
\item
  \emph{Brazilian space program}
\item
  \emph{Brazilian National Institute for Space Research}
\item
  \emph{Marcos Pontes, the first Brazilian in space}
\end{itemize}

Brazilian Organization for the Development of Aeronautical Certification

Brazilian Space Agency

Brazilian space program

Brazilian National Institute for Space Research

List of aerospace flight test centres

Marcos Pontes, the first Brazilian in space

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Coordinates: 23°12′34.78″S 45°52′17.18″W﻿ / ﻿23.2096611°S
  45.8714389°W﻿ / -23.2096611; -45.8714389}
\item
  \emph{CTA homepage}
\item
  \emph{IAE homepage}
\item
  \emph{IFI homepage}
\end{itemize}

CTA homepage

IAE homepage

IFI homepage

Coordinates: 23°12′34.78″S 45°52′17.18″W﻿ / ﻿23.2096611°S 45.8714389°W﻿
/ -23.2096611; -45.8714389
