\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Deputy\%20Administrator\%20of\%20NASA\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{List of Administrators and Deputy Administrators of
NASA}\label{list-of-administrators-and-deputy-administrators-of-nasa}

\begin{itemize}
\item
  \emph{According to NASA, the role of the Administrator is to "lead the
  NASA team and manage its resources to advance the Vision for Space
  Exploration."}
\item
  \emph{The Administrator and Deputy Administrator of NASA are the
  highest-ranked officials of NASA, the space agency of the United
  States Federal Government.}
\item
  \emph{Dr. Daniel Mulville served as the acting Deputy Administrator
  twice, and was acting Administrator in between.}
\end{itemize}

The Administrator and Deputy Administrator of NASA are the
highest-ranked officials of NASA, the space agency of the United States
Federal Government. The Administrator serves as the senior space science
advisor to the President of the United States. According to NASA, the
role of the Administrator is to "lead the NASA team and manage its
resources to advance the Vision for Space Exploration." The Deputy
Administrator of NASA "serves as the agency's second in command and is
responsible to the administrator for providing overall leadership,
planning, and policy direction for the agency. They represent NASA to
the Executive Office of the President, Congress, heads of federal and
other appropriate government agencies, international organizations, and
external organizations and communities. They also oversee the day to day
work of NASA's functional offices, such as the Office of the Chief
Financial Officer, Office of General Counsel and Strategic
Communications", according to NASA (referring to Shana Dale).

The first Administrator of NASA was Dr. T. Keith Glennan; during his
term he brought together the disparate projects in space development
research in the US. Daniel Goldin held the post for the longest term
(nearly 10 years), and is best known for pioneering the "faster, better,
cheaper" approach to space programs. The only person to hold the post
twice is James C. Fletcher, who returned to NASA following the
Challenger disaster.

The longest-running (acting) Deputy Administrator was John R. Dailey,
who held the post following his retirement from the United States Marine
Corps. The longest-running full Deputy Administrator was Hugh Latimer
Dryden, who was the first Deputy Administrator. William R. Graham has
held the post of Deputy Administrator twice, and was the acting
Administrator in between, as did Frederick D. Gregory. Dr. Daniel
Mulville served as the acting Deputy Administrator twice, and was acting
Administrator in between.

The current Administrator is Jim Bridenstine, who was nominated by
President Donald Trump on September 1, 2017. Bridenstine was confirmed
on April 19, 2018, and was sworn in four days later on April 23, 2018.

\section{Administrators}\label{administrators}

\begin{itemize}
\item
  \emph{Status}
\end{itemize}

Status

\section{Deputy Administrators}\label{deputy-administrators}

\section{Line of succession}\label{line-of-succession}

\begin{itemize}
\item
  \emph{Deputy Administrator of NASA}
\item
  \emph{In the event of there being no Deputy Administrator of NASA, and
  the Associate Administrator serving as Acting Administrator, then the
  Deputy Associate Administrator assumes the role of Acting Deputy
  Administrator.}
\item
  \emph{Associate Administrator of NASA- Deputy Associate Administrator
  of NASA (if applicable)}
\end{itemize}

The line of succession for the Administrator of the National Aeronautics
and Space Administration is as follows:

Deputy Administrator of NASA

Associate Administrator of NASA- Deputy Associate Administrator of NASA
(if applicable)

Chief of Staff to the NASA Administrator

Director of Johnson Space Center (Houston, Texas)

Director of Kennedy Space Center (Merritt Island, Florida)

Director of Marshall Space Flight Center (Redstone Arsenal, Alabama)

In the event of there being no Deputy Administrator of NASA, and the
Associate Administrator serving as Acting Administrator, then the Deputy
Associate Administrator assumes the role of Acting Deputy Administrator.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{NASA Chief Scientist}
\end{itemize}

Chairmen of the National Advisory Committee for Aeronautics

NASA Chief Scientist

\section{References}\label{references}
