\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/DG\_\%28company\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{DG (company)}\label{dg-company}

\begin{itemize}
\item
  \emph{On February 7, 2014, DG's TV advertising business was acquired
  by Extreme Reach, Inc. and its online advertising business was spun
  off into the new company Sizmek, Inc.}
\item
  \emph{DG provided digital media commercial distribution services to
  the advertising, entertainment and broadcast industries with an online
  media distribution network used by advertisers and agencies, and
  online radio, television, cable, network and print publishing
  destinations.}
\end{itemize}

Invented and founded by John R. Armstrong then sold to Scott Ginsberg in
1993, Digital Generation Systems, Inc. (commonly referred to as DG) was
the very first National online service platform in the world. DG
provided digital media commercial distribution services to the
advertising, entertainment and broadcast industries with an online media
distribution network used by advertisers and agencies, and online radio,
television, cable, network and print publishing destinations. On
February 7, 2014, DG's TV advertising business was acquired by Extreme
Reach, Inc. and its online advertising business was spun off into the
new company Sizmek, Inc.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{All of DG's cash and working capital was then transferred to
  Sizmek and Extreme Reach acquired the remaining operations.}
\item
  \emph{DG temporarily changed its handle to DG FastChannel when DG
  Systems and FastChannel Networks merged in 2006.}
\item
  \emph{In 2011, DG began buying up digital ad serving technologies in
  the online space, specifically focused on Rich Media vendors with
  global reach.}
\end{itemize}

DG temporarily changed its handle to DG FastChannel when DG Systems and
FastChannel Networks merged in 2006.

DG Systems initially used POTs to distribute later adding web-based and
satellite technology for advertising content distribution thereby all
but eliminating the need for reel to reel audio tape and CDs for radio
station spot distribution. Later the system replaced the need for
videotape distribution for television. DG Systems created a hybrid
system that allowed for content delivery through either the satellite
distribution system or through the Internet.

FastChannel Networks used the Internet for delivery of content.
FastChannel Networks created a Web-based interface for developing,
managing and delivering advertising content. Using the Web, post houses,
advertisers and agencies were able to collaborate, manage and distribute
advertising content through an online application.

In 2009, DG was ranked fifth on the Fortune Small Business list of the
US' 100 Fastest Growing Small Public Companies. It also ranked fifth on
the 2009 Fortune Fastest Growing Companies in the World listing.

In 2011, DG began buying up digital ad serving technologies in the
online space, specifically focused on Rich Media vendors with global
reach. Such companies include Mediamind Technologies, EyeWonder and the
Unicast platform.

In 2011, DG was responsible for the first second-screen ad being served
in connection with Channel 4's Million Pound Drop TV game show. The
second screen ad format was watched by 20\% of the online playing
audience according to Dean Donaldson, Global Head of Media Innovation.

In August 2013, DG agreed to spin off their online ad tech operations
(branded as DG MediaMind and consisting of the merged operations of the
former MediaMind, EyeWonder, Unicast, Peer39, and Republic Project) into
a new company named Sizmek, Inc. and to sell their remaining operations
to Extreme Reach in a deal valued at \$485 million. The money was used
to pay off all of DG's debt and to fund a \$3/share dividend to
shareholders. All of DG's cash and working capital was then transferred
to Sizmek and Extreme Reach acquired the remaining operations. The deal
closed on February 7, 2014.

In March 2019, Sizmek has filed for Chapter 11 bankruptcy.

\section{Network Reach}\label{network-reach}

\begin{itemize}
\item
  \emph{DG soon moved its headquarters to Irving, Texas.}
\item
  \emph{In 2011, MediaMind, the online division of DG at the time, was
  the second largest online ad Server behind Google, reaching 700
  million unique users, as accredited by the Media Rating Council.}
\end{itemize}

DG soon moved its headquarters to Irving, Texas. Regional offices
included New York, Chicago, Los Angeles, San Francisco, Boca Raton,
Atlanta, Dallas, Detroit, Louisville, Toronto, London, and Herzliya in
Israel.

In 2011, MediaMind, the online division of DG at the time, was the
second largest online ad Server behind Google, reaching 700 million
unique users, as accredited by the Media Rating Council.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{CNN Money, Fortune 500 Listing}
\end{itemize}

CNN Money, Fortune 500 Listing
