\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Eden\_Taylor-Draper\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Eden Taylor-Draper}\label{eden-taylor-draper}

\begin{itemize}
\item
  \emph{Eden Elenor Taylor-Draper (born 28 October 1997) is an English
  actress.}
\item
  \emph{She plays Belle Dingle in the ITV soap opera Emmerdale, a role
  she took over from Emily Mather in 2005.}
\end{itemize}

Eden Elenor Taylor-Draper (born 28 October 1997) is an English actress.
She plays Belle Dingle in the ITV soap opera Emmerdale, a role she took
over from Emily Mather in 2005.

\section{Emmerdale}\label{emmerdale}

\begin{itemize}
\item
  \emph{One of Taylor-Draper's notable storylines in Emmerdale was when
  Belle fell down a mineshaft on Christmas Day 2005.}
\item
  \emph{She and Luke Tittensor won the 'Spectacular Scene of the Year'
  award at the 2006 British Soap Awards for this storyline.}
\end{itemize}

One of Taylor-Draper's notable storylines in Emmerdale was when Belle
fell down a mineshaft on Christmas Day 2005. She and Luke Tittensor won
the 'Spectacular Scene of the Year' award at the 2006 British Soap
Awards for this storyline. She was commended by fellow cast members for
her 2014 storyline involving the death of her character's best friend
Gemma (Tendai Rinomhota) and its aftermath.{[}citation needed{]}

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{On 11 September 2016, alongside her Emmerdale co-star Matthew
  Wolfenden, Taylor-Draper took part in the Great North Run to raise
  funds for Bloodwise.}
\end{itemize}

On 11 September 2016, alongside her Emmerdale co-star Matthew Wolfenden,
Taylor-Draper took part in the Great North Run to raise funds for
Bloodwise.

\section{Awards}\label{awards}

\begin{itemize}
\item
  \emph{Nominated for Best Young actress at the Inside Soap Awards in
  September 2008}
\item
  \emph{Won 'Best Dramatic Performance from a Young Actor or Actress' at
  the 2007 British Soap Awards.}
\item
  \emph{Won the title of 'Best Young Actor' at the Inside Soap Awards on
  24 September 2007.}
\item
  \emph{Won 'Best Young Performance' at the British Soap Awards 2013.}
\end{itemize}

Won the 2006 title of 'Most Spectacular Scene' along with co-star Luke
Tittensor (Daz Eden in Emmerdale) and Emmerdale crew members Neil
Alderton and Brian Morgan.

Nominated for the 'Best Young Actor' award at the 2006 Inside Soap
awards; lost to young Hollyoaks actor Ellis Hollins.

Won 'Best Dramatic Performance from a Young Actor or Actress' at the
2007 British Soap Awards.

Won the title of 'Best Young Actor' at the Inside Soap Awards on 24
September 2007.

Won the 'Personality of the year' award at the Yorkshire Young Achievers
Awards 2007.

Nominated for 'Best Dramatic Performance from a Young Actor or Actress'
at the British Soap Awards 2008.

Nominated for Best Young actress at the Inside Soap Awards in September
2008

Won 'Best Young Performance' at the British Soap Awards 2013.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Eden Taylor-Draper on IMDb}
\end{itemize}

Eden Taylor-Draper on IMDb
