\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Fuleswari\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Fuleswari}\label{fuleswari}

\begin{itemize}
\item
  \emph{\\[4\baselineskip]Fuleswari is a Bengali romance drama film
  directed by Tarun Majumdar based on a story of Bibhutibhushan
  Bandyopadhyay.}
\item
  \emph{Hemanta Mukhopadhyay was the music director of the film.}
\end{itemize}

Fuleswari is a Bengali romance drama film directed by Tarun Majumdar
based on a story of Bibhutibhushan Bandyopadhyay. This film was released
on 3 May 1974 under the banner of Radharani Pictures. Hemanta
Mukhopadhyay was the music director of the film.

\section{Plot}\label{plot}

\begin{itemize}
\item
  \emph{She plans to marry him but is hesitant when she learns that
  Brindaban is involved in a crime.}
\item
  \emph{Fuleswari, a young woman, falls in love with Brindaban, who
  arrives in her village.}
\end{itemize}

Fuleswari, a young woman, falls in love with Brindaban, who arrives in
her village. She plans to marry him but is hesitant when she learns that
Brindaban is involved in a crime.

\section{Cast}\label{cast}

\begin{itemize}
\item
  \emph{Samit Bhanja as Brindaban}
\item
  \emph{Sandhya Roy as Fuleswari}
\end{itemize}

Sandhya Roy as Fuleswari

Samit Bhanja as Brindaban

Utpal Dutt

Rabi Ghosh

Anup Kumar

Tarun Kumar

Lily Chakravarty

Sulata Chowdhury

Molina Devi

Gita Dey

Ashim Chakraborty

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Fuleswari on IMDb}
\end{itemize}

Fuleswari on IMDb
