\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Giorgi\_Aburjania\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Giorgi Aburjania}\label{giorgi-aburjania}

\begin{itemize}
\item
  \emph{: giorgi aburjania, pronounced~{[}ɡiɔrɡi ɑburd͡ʒɑniɑ{]}; born 2
  January 1995) is a Georgian professional footballer who plays for
  Spanish club CD Lugo on loan from Sevilla FC as a central midfielder.}
\item
  \emph{Giorgi Aburjania (Georgian: გიორგი აბურჯანია, translit.}
\end{itemize}

Giorgi Aburjania (Georgian: გიორგი აბურჯანია, translit.: giorgi
aburjania, pronounced~{[}ɡiɔrɡi ɑburd͡ʒɑniɑ{]}; born 2 January 1995) is a
Georgian professional footballer who plays for Spanish club CD Lugo on
loan from Sevilla FC as a central midfielder.

\section{Club career}\label{club-career}

\begin{itemize}
\item
  \emph{Aburjania kicked off his career with Metalurgi Rustavi in 2010.}
\item
  \emph{On 1 August 2018, after suffering relegation, Aburjania was
  loaned to fellow second division side CD Lugo, for one year.}
\item
  \emph{On 8 January 2016 Aburjania moved to Spain, after agreeing to a
  three-and-a-half year contract with Segunda División side Gimnàstic de
  Tarragona.}
\end{itemize}

Aburjania kicked off his career with Metalurgi Rustavi in 2010. He then
had stints with Dila and Lokomotivi Tbilisi. On 17 June 2014, he signed
for Cypriot club Anorthosis Famagusta on a two-year contract.

On 8 January 2016 Aburjania moved to Spain, after agreeing to a
three-and-a-half year contract with Segunda División side Gimnàstic de
Tarragona. He made his debut for the club late in the month, coming on
as a second-half substitute for Lévy Madinda in a 2--1 home win against
CD Tenerife.

Aburjania subsequently became an undisputed starter for Vicente Moreno's
side, and scored his first goal for the club on 20 March 2016 in a 4--0
away routing of Bilbao Athletic. On 2 August he signed a four-year
contract with Sevilla FC, being assigned to the reserves also in the
second division, for a rumoured fee of \euro{} 1 million.

On 1 August 2018, after suffering relegation, Aburjania was loaned to
fellow second division side CD Lugo, for one year.

\section{International career}\label{international-career}

\begin{itemize}
\item
  \emph{After representing Georgia at under-17, under-19 and under-21
  levels, Aburjania made his debut with the full squad on 29 March 2016,
  starting in a 1--1 friendly draw against Kazakhstan.}
\end{itemize}

After representing Georgia at under-17, under-19 and under-21 levels,
Aburjania made his debut with the full squad on 29 March 2016, starting
in a 1--1 friendly draw against Kazakhstan.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Giorgi Aburjania at National-Football-Teams.com}
\item
  \emph{Giorgi Aburjania -- UEFA competition record}
\item
  \emph{Giorgi Aburjania at Soccerway}
\end{itemize}

Giorgi Aburjania -- UEFA competition record

Giorgi Aburjania at National-Football-Teams.com

Giorgi Aburjania at Soccerway
