\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/How\%20Long\%2C\%20Not\%20Long\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{How Long, Not Long}\label{how-long-not-long}

\begin{itemize}
\item
  \emph{"How Long, Not Long" is the popular name given to the public
  speech delivered by Martin Luther King Jr. on the steps of the State
  Capitol in Montgomery, Alabama, after the successful completion of the
  Selma to Montgomery March on March 25, 1965.}
\end{itemize}

"How Long, Not Long" is the popular name given to the public speech
delivered by Martin Luther King Jr. on the steps of the State Capitol in
Montgomery, Alabama, after the successful completion of the Selma to
Montgomery March on March 25, 1965. The speech is also sometimes
referred to as "Our God Is Marching On!"

\section{Key excerpts}\label{key-excerpts}

\begin{itemize}
\item
  \emph{(Yes, sir)"}
\item
  \emph{(Yes, sir) How long?}
\item
  \emph{Not long, (Yes, sir) because "no lie can live forever."}
\item
  \emph{"How long?}
\item
  \emph{(Yes, sir) I come to say to you this afternoon, however
  difficult the moment, (Yes, sir) however frustrating the hour, it will
  not be long, (No sir) because "truth crushed to earth will rise
  again."}
\item
  \emph{(Yes, sir.}
\item
  \emph{Yes, sir.}
\end{itemize}

"Last Sunday, more than eight thousand of us started on a mighty walk
from Selma, Alabama. We have walked through desolate valleys and across
the trying hills. We have walked on meandering highways and rested our
bodies on rocky byways. Some of our faces are burned from the
outpourings of the sweltering sun. Some have literally slept in the mud.
We have been drenched by the rains. {[}Audience:{]} (Speak) Our bodies
are tired and our feet are somewhat sore."

"Now it is not an accident that one of the great marches of American
history should terminate in Montgomery, Alabama. (Yes, sir) Just ten
years ago, in this very city, a new philosophy was born of the Negro
struggle. Montgomery was the first city in the South in which the entire
Negro community united and squarely faced its age-old oppressors. (Yes,
sir. Well)"

"They told us we wouldn't get here. And there were those who said that
we would get here only over their dead bodies, (Well. Yes, sir. Talk)
but all the world today knows that we are here and we are standing
before the forces of power in the state of Alabama saying, "We ain't
goin' let nobody turn us around." (Yes, sir. Speak) {[}Applause{]}"

"Once more the method of nonviolent resistance (Yes) was unsheathed from
its scabbard, and once again an entire community was mobilized to
confront the adversary. (Yes, sir) And again the brutality of a dying
order shrieks across the land. Yet, Selma, Alabama, became a shining
moment in the conscience of man. If the worst in American life lurked in
its dark street, the best of American instincts arose passionately from
across the nation to overcome it."

"The battle is in our hands. And we can answer with creative nonviolence
the call to higher ground to which the new directions of our struggle
summons us. (Yes, sir) The road ahead is not altogether a smooth one.
(No) There are no broad highways that lead us easily and inevitably to
quick solutions. But we must keep going."

"Our aim must never be to defeat or humiliate the white man, but to win
his friendship and understanding. We must come to see that the end we
seek is a society at peace with itself, a society that can live with its
conscience. And that will be a day not of the white man, not of the
black man. That will be the day of man as man. (Yes)"

"I know you are asking today, "How long will it take?" (Speak, sir)
Somebody's asking, "How long will prejudice blind the visions of men,
darken their understanding, and drive bright-eyed wisdom from her sacred
throne?" Somebody's asking, "When will wounded justice, lying prostrate
on the streets of Selma and Birmingham and communities all over the
South, be lifted from this dust of shame to reign supreme among the
children of men?" Somebody's asking, "When will the radiant star of hope
be plunged against the nocturnal bosom of this lonely night, (Speak,
speak, speak) plucked from weary souls with chains of fear and the
manacles of death? How long will justice be crucified, (Speak) and truth
bear it?" (Yes, sir) I come to say to you this afternoon, however
difficult the moment, (Yes, sir) however frustrating the hour, it will
not be long, (No sir) because "truth crushed to earth will rise again."
(Yes, sir) How long? Not long, (Yes, sir) because "no lie can live
forever." (Yes, sir) How long? Not long, (All right. How long) because
"you shall reap what you sow." (Yes, sir)"

"How long? Not long, because the arc of the moral universe is long, but
it bends toward justice."

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Our God Is Marching On!}
\item
  \emph{complete text from mlkonline.net}
\end{itemize}

Our God Is Marching On! complete text from mlkonline.net
