\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Hudson\_Journal\_\%28magazine\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Hudson Journal (magazine)}\label{hudson-journal-magazine}

\begin{itemize}
\item
  \emph{Hudson Journal is a biannually printed publication based in New
  York.}
\item
  \emph{The magazine is being relaunched with a new design in 2019.}
\item
  \emph{It was founded in 2011 as Avenue Journal, with its second issue
  published by Mor치n Mor치n (formerly known as OHWOW).}
\end{itemize}

Hudson Journal is a biannually printed publication based in New York. It
was founded in 2011 as Avenue Journal, with its second issue published
by Mor치n Mor치n (formerly known as OHWOW). It is currently published and
edited by John Hudson White.

The magazine employs writers such as Rob Goyanes, Tereza Zelenkova, and
Szilvia Molnar, and has featured interviews with Alexandra Kleeman,
Franco Maria Ricci and Kostas Murkudis. The magazine is being relaunched
with a new design in 2019.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Avenue Journal at WorldCat}
\item
  \emph{Avenue Journal on Creative Director's website}
\item
  \emph{Avenue Journal at Models.com}
\item
  \emph{Website of Hudson Journal}
\end{itemize}

Website of Hudson Journal

Avenue Journal on Creative Director's website

Avenue Journal at Models.com

Avenue Journal at WorldCat
