\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Islam\_in\_Zanzibar\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Islam in Zanzibar}\label{islam-in-zanzibar}

\begin{itemize}
\item
  \emph{According to one source, "Islam in Zanzibar inspired
  anti-colonialism, political movements and nationalistic struggle for
  independence.}
\item
  \emph{Islam is the most prominent religion on the island of Zanzibar.}
\item
  \emph{Islam came to Zanzibar in the 8th century.}
\item
  \emph{There is also a presence of Ahmadi Muslims in Zanzibar.}
\end{itemize}

Islam is the most prominent religion on the island of Zanzibar.
According to the CIA Factbook, more than 99\% in the island are Muslim.
The vast majority of Muslims in Zanzibar are Sunni of Shafi'i school of
jurisprudence with minority Ibadi, Ismaili and Twelver Shia. Islam came
to Zanzibar in the 8th century. There is also a presence of Ahmadi
Muslims in Zanzibar.

According to one source, "Islam in Zanzibar inspired anti-colonialism,
political movements and nationalistic struggle for
independence."{[}citation needed{]}

\section{Notable Muslim clerics}\label{notable-muslim-clerics}

\begin{itemize}
\item
  \emph{Amir Tajir was the Chief qadi in Zanzibar.}
\item
  \emph{Nassor Bachoo was a well known Muslim cleric in East Africa,
  particularly in Tanzania and Kenya, while he was a controversial
  figure in Zanzibar.}
\item
  \emph{Other Muslim clerics include members of the Uamsho (the
  Association for Islamic Mobilisation and Propagation), whose mission
  is to fight for the secession of Zanzibar from the Union of the United
  Republic of Tanzania.}
\item
  \emph{Sh Abdullah Saleh Farsy was an internationally known poet,
  scholar and Muslim historian in Zanzibar.}
\end{itemize}

Sh Abdullah Saleh Farsy was an internationally known poet, scholar and
Muslim historian in Zanzibar.{[}citation needed{]} He is well known for
his contribution to Islamic knowledge, being first to translate the
Quran into the Swahili language.

Sh. Nassor Bachoo was a well known Muslim cleric in East Africa,
particularly in Tanzania and Kenya, while he was a controversial figure
in Zanzibar.{[}citation needed{]}

Other Muslim clerics include members of the Uamsho (the Association for
Islamic Mobilisation and Propagation), whose mission is to fight for the
secession of Zanzibar from the Union of the United Republic of Tanzania.

The late Sh. Amir Tajir was the Chief qadi in Zanzibar.

Ancient tomb at Tongo (1872 engraving)

Old Mosque on the beach, 1898

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{"Eco-Islam hits Zanzibar fishermen BBC News, 17 February 2005}
\item
  \emph{"ROLE OF ISLAM ON POLITICS IN ZANZIBAR" by Khatib A. Rajab}
\end{itemize}

"Eco-Islam hits Zanzibar fishermen BBC News, 17 February 2005

"ROLE OF ISLAM ON POLITICS IN ZANZIBAR" by Khatib A. Rajab
