\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Ivan\_Neumyvakin\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Ivan Neumyvakin}\label{ivan-neumyvakin}

\begin{itemize}
\item
  \emph{Ivan Pavlovich Neumyvakin (Russian: Иван Павлович Неумывакин;
  Jule 7, 1928, near Bishkek, Kyrgyzstan -- April 22, 2018,
  Moscow{[}citation needed{]}, Russia) was a Russian physician, Doctor
  of Medical Sciences, Professor and Fellow of the Russian Academy of
  Natural Sciences.}
\end{itemize}

Ivan Pavlovich Neumyvakin (Russian: Иван Павлович Неумывакин; Jule 7,
1928, near Bishkek, Kyrgyzstan -- April 22, 2018, Moscow{[}citation
needed{]}, Russia) was a Russian physician, Doctor of Medical Sciences,
Professor and Fellow of the Russian Academy of Natural Sciences.\\
Laureate of the 1982 Latvian SSR State Prize and of the 2005
``Profession - Life'' International Prize.\\
He is known in Russia as one of the founders of space medicine. He also
is known as a healer.\\
He received the honorary titles 1979 "Honoured Inventor of the RSFSR"
and the 2006 "The Person of Russia" and the title "Distinguished Healer
of the Russia" (Лучший народный целитель России) and the title ``Maitre
of Science and Practice''.\\
He was a popular author.\\
His book Endoecology of health is a best seller.\\
Marie Claire magazine named him "Guru of healthy lifestyle".

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{He was vice president of the Russian Association of folk
  medicine (РАНМ) since 2012.}
\item
  \emph{He also was Academician of the International Informatization
  Academy and of the European Academy of Natural Sciences and of the
  Academy of Medical and Technical Sciences and of the International
  Charity Academy (since 2010).}
\end{itemize}

He was born on the family farm.\\
His mother was healer.\\
He graduated from the Kyrgyz State Medical Academy in 1951.\\
He was a surgeon and served for eight years in the Far East.\\
From 1964 until 1989, he worked at the Institute of Medicobiological
Problems of the Russian Academy of Sciences.\\
In 1965, he defended his Candidate's Dissertation.\\
He was a student of Boris Evgenyevich Votchal.\\
In 1982, he defended his doctoral dissertation.\\
In 1989, he retired and then he headed his medical Center.\\
His rank is Colonel.

He was vice president of the Russian Association of folk medicine (РАНМ)
since 2012.\\
He was the Chairman of the Academic council of this Association after
its reorganization.\\
He was a member of the Bureau of the Academic Council of the All-Russian
Research Center for Traditional Folk Medicine.\\
He was an assistant to the deputy of the State Duma of the Russian
Federation.\\
He was a Member of the Presidium of The 100 Years Club (as well as his
friend Nikolay Drozdov).

He also was Academician of the International Informatization Academy and
of the European Academy of Natural Sciences and of the Academy of
Medical and Technical Sciences and of the International Charity Academy
(since 2010).

He was a Honorary Member of the "Generals of the World for Peace"
International Association (since 2014). He was given the Medal of this
Association in 2016 for peacemaking activities.

I.P. Neumyvakin received the Order of Holy Prince Daniel of Moscow, from
Patriarch Alexy II of Moscow.

I.P. Neumyvakin is the author of more than 250 scientific papers. He
also is the author about 100 books. He has about 100 inventions.

His wife, Lyudmila Stepanovna, was also a physician.

\section{Honors and awards}\label{honors-and-awards}

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Members of the presidential council of the Russian Association
  of folk medicine (РАНМ)}
\end{itemize}

ResearchGate

Members of the presidential council of the Russian Association of folk
medicine (РАНМ)

`I am Ashamed to Listen to Our Cardiologists' // Pravda.ru, 2002.

The only health center in Russia of Professor Neumyvakin begins work in
the village of Malorechenskoe near Alushta // Crimea Travel Portal by
Ministry of Resorts \& Tourism, 29 September 2017.

Болезней не существует: правила здоровья Ивана Неумывакина // «Marie
Claire»
