\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Jake\_Smith\_\%28pitcher\%2C\_born\_1887\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Jake Smith (pitcher, born
1887)}\label{jake-smith-pitcher-born-1887}

\begin{itemize}
\item
  \emph{Jacob John "Jake" Smith (June 10, 1887 -- November 7, 1948) was
  a professional baseball player.}
\item
  \emph{A relief pitcher, Smith appeared in two games for the
  Philadelphia Phillies of Major League Baseball's National League
  during the 1911 season.}
\end{itemize}

Jacob John "Jake" Smith (June 10, 1887 -- November 7, 1948) was a
professional baseball player. A relief pitcher, Smith appeared in two
games for the Philadelphia Phillies of Major League Baseball's National
League during the 1911 season. He was officially listed as standing
6~feet 5~inches (196~cm) and weighing 200 pounds (91~kg).

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{While fielding on the mound, Smith had a perfect 1.000 fielding
  percentage, making two assists in his two fielding chances.}
\item
  \emph{In 1911, Smith played two games for the Philadelphia Phillies.}
\item
  \emph{As a hitter, Smith made three plate appearances in his two
  games.}
\item
  \emph{Smith was born "Jacob Schmidt" on June 10, 1887, in Dravosburg,
  Pennsylvania.}
\end{itemize}

Smith was born "Jacob Schmidt" on June 10, 1887, in Dravosburg,
Pennsylvania.

In 1911, Smith played two games for the Philadelphia Phillies. In his
two games as a pitcher, he finished both games in which he played,
meaning that he completed the final inning in each. He threw a total of
five innings in those contests. He faced 19 batters, of whom he struck
out one and walked two. Having allowed three hits to supplement his two
free passes, he amassed a WHIP ratio (walks plus hits per inning
pitched) of 1.000.

As a hitter, Smith made three plate appearances in his two games. He did
not collect any hits in those three times at bat, but did earn a single
run batted in. While fielding on the mound, Smith had a perfect 1.000
fielding percentage, making two assists in his two fielding chances.

Smith died on November 7, 1948, across the river from his hometown in
East McKeesport, Pennsylvania, at age 61. He was interred in Grandview
Cemetery in McKeesport, Pennsylvania.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Philadelphia Phillies all-time roster (S)}
\end{itemize}

Philadelphia Phillies all-time roster (S)

"Cup of coffee" --- a short stint at the major league level of a sport

List of people from the Pittsburgh metropolitan area

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Career statistics and player information from
  Baseball-Reference, or~Fangraphs}
\end{itemize}

Career statistics and player information from Baseball-Reference,
or~Fangraphs
