\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/James\_Parker\_\%28Massachusetts\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{James Parker (Massachusetts)}\label{james-parker-massachusetts}

\begin{itemize}
\item
  \emph{Parker represented Massachusetts's 19th district in the United
  States House of Representatives from 1813 to 1815, and the 18th
  district from 1819 to 1821.}
\end{itemize}

James Parker (1768-- November 9, 1837) was an American politician.

Parker was born and educated in Boston. He studied medicine, became a
doctor, and started a practice in Gardiner, Maine when Maine was part of
Massachusetts.

In addition to practicing medicine, Parker was an inventor, and received
a patent for an improved brick and tile making process.

Active in politics as a Democratic-Republican, he served in the
Massachusetts State Senate from 1811 to 1812. Parker represented
Massachusetts's 19th district in the United States House of
Representatives from 1813 to 1815, and the 18th district from 1819 to
1821.

In 1824 Parker was chosen as a presidential elector pledged to support
John Quincy Adams.

Parker died in Gardiner on November 9, 1837 and was buried at Gardiner's
Oak Grove Cemetery.

\section{References}\label{references}

\section{Sources}\label{sources}

\begin{itemize}
\item
  \emph{"James Parker (id: P000060)".}
\end{itemize}

United States Congress. "James Parker (id: P000060)". Biographical
Directory of the United States Congress..mw-parser-output
cite.citation\{font-style:inherit\}.mw-parser-output .citation
q\{quotes:"\textbackslash{}"""\textbackslash{}"""'""'"\}.mw-parser-output
.citation .cs1-lock-free
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/6/65/Lock-green.svg/9px-Lock-green.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .citation .cs1-lock-limited
a,.mw-parser-output .citation .cs1-lock-registration
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/d/d6/Lock-gray-alt-2.svg/9px-Lock-gray-alt-2.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .citation .cs1-lock-subscription
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/a/aa/Lock-red-alt-2.svg/9px-Lock-red-alt-2.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .cs1-subscription,.mw-parser-output
.cs1-registration\{color:\#555\}.mw-parser-output .cs1-subscription
span,.mw-parser-output .cs1-registration span\{border-bottom:1px
dotted;cursor:help\}.mw-parser-output .cs1-ws-icon
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/4/4c/Wikisource-logo.svg/12px-Wikisource-logo.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output
code.cs1-code\{color:inherit;background:inherit;border:inherit;padding:inherit\}.mw-parser-output
.cs1-hidden-error\{display:none;font-size:100\%\}.mw-parser-output
.cs1-visible-error\{font-size:100\%\}.mw-parser-output
.cs1-maint\{display:none;color:\#33aa33;margin-left:0.3em\}.mw-parser-output
.cs1-subscription,.mw-parser-output .cs1-registration,.mw-parser-output
.cs1-format\{font-size:95\%\}.mw-parser-output
.cs1-kern-left,.mw-parser-output
.cs1-kern-wl-left\{padding-left:0.2em\}.mw-parser-output
.cs1-kern-right,.mw-parser-output
.cs1-kern-wl-right\{padding-right:0.2em\}
