\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Joseph\%20Ellwanger\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Joseph Ellwanger}\label{joseph-ellwanger}

\begin{itemize}
\item
  \emph{He was a key figure in the Civil Rights Movement in Birmingham,
  Alabama, and the only white religious leader included in strategy
  meetings with Martin Luther King, Jr.}
\item
  \emph{1934) is a Lutheran pastor, author and civil rights activist.}
\item
  \emph{Pastor Joseph "Joe" W. Ellwanger, Jr. (b.}
\end{itemize}

Pastor Joseph "Joe" W. Ellwanger, Jr. (b. 1934) is a Lutheran pastor,
author and civil rights activist. He was a key figure in the Civil
Rights Movement in Birmingham, Alabama, and the only white religious
leader included in strategy meetings with Martin Luther King, Jr.

\section{Early life and education}\label{early-life-and-education}

\begin{itemize}
\item
  \emph{Born in 1934, Ellwanger spent part of his childhood in Selma,
  Alabama, where his father was a pastor and President of Alabama
  Lutheran Academy and College.}
\item
  \emph{Ellwanger graduated from Concordia Seminary.}
\end{itemize}

Born in 1934, Ellwanger spent part of his childhood in Selma, Alabama,
where his father was a pastor and President of Alabama Lutheran Academy
and College. Ellwanger graduated from Concordia Seminary.

\section{Career}\label{career}

\begin{itemize}
\item
  \emph{It is the highest honor bestowed on an individual by the
  Birmingham Civil Rights Institute.}
\item
  \emph{During that time, Ellwanger became colleagues with Martin Luther
  King, Jr.}
\item
  \emph{In 2008, Ellwanger was named as the recipient of the Fred L.
  Shuttlesworth Human Rights Award.}
\item
  \emph{Ellwanger was the only white minister in Birmingham who took
  such an active role in supporting equal rights for African Americans.}
\end{itemize}

From 1958 to 1967, Ellwanger served as pastor of the African-American
church St. Paul Lutheran in Birmingham. During that time, Ellwanger
became colleagues with Martin Luther King, Jr.

Ellwanger answered the call of King and the Southern Christian
Leadership Conference to recruit students and clergy to join the
movement in Selma to take part in the march for voting rights from Selma
to the state capital of Montgomery. Ellwanger took part in mass
meetings, involving himself and members of his congregation in Civil
Rights activities, and ultimately took a leadership role in community
organizing. Ellwanger helped Martin Luther King, Jr. and others plan the
Birmingham demonstrations and helped organize the Saturday, March 6,
1965 march in Selma, Alabama to support voting rights.

Ellwanger was the only white minister in Birmingham who took such an
active role in supporting equal rights for African Americans. Ellwanger
spoke at the funeral for one of the four girls who was killed in the
church bombing, where Dr. King delivered the eulogy.

King included Ellwanger in a group of 15 pastors that met with Governor
George Wallace. Ellwanger also met with President Lyndon B. Johnson to
voice support for the Voting Rights Act of 1965.

In 1967, Ellwanger left for Milwaukee, Wisconsin where he served as
Pastor of Cross Lutheran Church until 2001. In 1969, Ellwanger worked
with the Black Panther Party to expand the free breakfast program in
Milwaukee. In 1970, Ellwanger founded the prison ministry "Project
RETURN," with the mission of aiding and rehabilitating citizens
returning from incarceration. After retiring from Cross Lutheran,
Ellwanger spent a decade as a grassroots organizer for WISDOM, a
statewide coalition of social justice groups in Wisconsin. Ellwanger
founded WISDOM's statewide Reform Our Communities (ROC) Campaign to
reform Wisconsin's criminal justice system.

In 2008, Ellwanger was named as the recipient of the Fred L.
Shuttlesworth Human Rights Award. It is the highest honor bestowed on an
individual by the Birmingham Civil Rights Institute.

Ellwanger was a recipient of the 2016 Social Innovation Prize from
Interfaith Older Adult Programs. The award included \$10,000 to continue
his work to end mass incarceration in Wisconsin.

\section{Books}\label{books}

\begin{itemize}
\item
  \emph{Ellwanger has been a subject in a number of books, including
  King: A Biography by David Levering Lewis, Eyes on the Prize:
  America's Civil Rights Years, 1954-1965 by Juan Williams, Kids in
  Birmingham 1963, and On the Road to Freedom: A Guided Tour of the
  Civil Rights Trail by Charles E. Cobb Jr.}
\item
  \emph{Strength for the Struggle: Insights from the Civil Rights
  Movement and Urban Ministry.}
\item
  \emph{Pastor Joseph Ellwanger (2014-12-10).}
\end{itemize}

Ellwanger has been a subject in a number of books, including King: A
Biography by David Levering Lewis, Eyes on the Prize: America's Civil
Rights Years, 1954-1965 by Juan Williams, Kids in Birmingham 1963, and
On the Road to Freedom: A Guided Tour of the Civil Rights Trail by
Charles E. Cobb Jr.

Pastor Joseph Ellwanger (2014-12-10). Strength for the Struggle:
Insights from the Civil Rights Movement and Urban Ministry. HenschelHAUS
Publishing. ISBN~978-1-595-98296-4..mw-parser-output
cite.citation\{font-style:inherit\}.mw-parser-output .citation
q\{quotes:"\textbackslash{}"""\textbackslash{}"""'""'"\}.mw-parser-output
.citation .cs1-lock-free
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/6/65/Lock-green.svg/9px-Lock-green.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .citation .cs1-lock-limited
a,.mw-parser-output .citation .cs1-lock-registration
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/d/d6/Lock-gray-alt-2.svg/9px-Lock-gray-alt-2.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .citation .cs1-lock-subscription
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/a/aa/Lock-red-alt-2.svg/9px-Lock-red-alt-2.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output .cs1-subscription,.mw-parser-output
.cs1-registration\{color:\#555\}.mw-parser-output .cs1-subscription
span,.mw-parser-output .cs1-registration span\{border-bottom:1px
dotted;cursor:help\}.mw-parser-output .cs1-ws-icon
a\{background:url("//upload.wikimedia.org/wikipedia/commons/thumb/4/4c/Wikisource-logo.svg/12px-Wikisource-logo.svg.png")no-repeat;background-position:right
.1em center\}.mw-parser-output
code.cs1-code\{color:inherit;background:inherit;border:inherit;padding:inherit\}.mw-parser-output
.cs1-hidden-error\{display:none;font-size:100\%\}.mw-parser-output
.cs1-visible-error\{font-size:100\%\}.mw-parser-output
.cs1-maint\{display:none;color:\#33aa33;margin-left:0.3em\}.mw-parser-output
.cs1-subscription,.mw-parser-output .cs1-registration,.mw-parser-output
.cs1-format\{font-size:95\%\}.mw-parser-output
.cs1-kern-left,.mw-parser-output
.cs1-kern-wl-left\{padding-left:0.2em\}.mw-parser-output
.cs1-kern-right,.mw-parser-output
.cs1-kern-wl-right\{padding-right:0.2em\}

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Author's web site for Strength for the Struggle}
\end{itemize}

Author's web site for Strength for the Struggle
