\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Kosovo\_women\%27s\_national\_football\_team\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Kosovo women's national football
team}\label{kosovo-womens-national-football-team}

\begin{itemize}
\item
  \emph{The Kosovo women's national football team (Albanian: Kombëtarja
  e futbollit të femrave të Kosovës, Serbian: Женска фудбалска
  репрезентација Косова/Ženska fudbalska reprezentacija Kosova)
  represents Kosovo in international women's football and is controlled
  by the Football Federation of Kosovo.}
\end{itemize}

The Kosovo women's national football team (Albanian: Kombëtarja e
futbollit të femrave të Kosovës, Serbian: Женска фудбалска
репрезентација Косова/Ženska fudbalska reprezentacija Kosova) represents
Kosovo in international women's football and is controlled by the
Football Federation of Kosovo.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{On 3 May 2016 at the Ordinary Congress, Kosovo were accepted
  into UEFA after members voted 28--24 in favor of Kosovo.}
\end{itemize}

In 2010, the national team is established. On 6 February 2013, FIFA gave
the permission to play international friendly games against other member
associations.

On 3 May 2016 at the Ordinary Congress, Kosovo were accepted into UEFA
after members voted 28--24 in favor of Kosovo.

\section{Match record}\label{match-record}

\begin{itemize}
\item
  \emph{On 9 January 2017, the national team for the first time was able
  to enter tournaments organized by FIFA and will play their first
  competitive matches in the qualification rounds for the 2019 FIFA
  Women's World Cup.}
\item
  \emph{On 1 March 2017.}
\item
  \emph{Kosovo played its first international match as FIFA member, in
  the framework of a tournament against Poland.}
\end{itemize}

On 1 March 2017. Kosovo played its first international match as FIFA
member, in the framework of a tournament against Poland. The match ended
in a 0--5 defeat. On 9 January 2017, the national team for the first
time was able to enter tournaments organized by FIFA and will play their
first competitive matches in the qualification rounds for the 2019 FIFA
Women's World Cup.

\section{FIFA Women's World Cup}\label{fifa-womens-world-cup}

\section{UEFA Women's Championship}\label{uefa-womens-championship}

\section{Turkish Women's Cup}\label{turkish-womens-cup}

\begin{itemize}
\item
  \emph{Kosovo was invited for first time to the Turkish Women's Cup.}
\end{itemize}

In 2017. Kosovo was invited for first time to the Turkish Women's Cup.
They were sorted into a group with Poland, Romania and Turkey and ended
the last with 3 defeats.

\section{Fixtures and results}\label{fixtures-and-results}

\begin{itemize}
\item
  \emph{For all past match results of the women's national team, see
  single-season articles and the team's results page}
\end{itemize}

For all past match results of the women's national team, see
single-season articles and the team's results page

\section{2018}\label{section}

\section{2019}\label{section-1}

\section{2020}\label{section-2}

\section{Players}\label{players}

\section{Current squad}\label{current-squad}

\begin{itemize}
\item
  \emph{The following players have been called up for the friendly
  matches against ~North Macedonia, on 5 and 8 April 2019.All caps and
  goals as of 5 April 2019 after match against ~North Macedonia, only
  matches as FIFA member are included.}
\end{itemize}

The following players have been called up for the friendly matches
against ~North Macedonia, on 5 and 8 April 2019.All caps and goals as of
5 April 2019 after match against ~North Macedonia, only matches as FIFA
member are included.{[}a{]}\\
.mw-parser-output .nat-fs-player
th\{background-color:inherit;border:0\}.mw-parser-output .nat-fs-player
td\{text-align:center;border:0\}

\section{Recent call-ups}\label{recent-call-ups}

\begin{itemize}
\item
  \emph{The following players have been called up for the team within
  the last 12 months and are still available for selection.}
\end{itemize}

The following players have been called up for the team within the last
12 months and are still available for selection.

Notes

INJ = Not part of the current squad due to injury.

\section{Coaching staff}\label{coaching-staff}

\section{Head-to-head records against other
countries}\label{head-to-head-records-against-other-countries}

\begin{itemize}
\item
  \emph{As of 9 November 2018Head-to-head records are included only
  matches as FIFA member.}
\end{itemize}

As of 9 November 2018Head-to-head records are included only matches as
FIFA member.

\section{Notes and references}\label{notes-and-references}

\section{Notes}\label{notes}

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Kosovo (women) News about the team}
\end{itemize}

Official website (in Albanian) ‹See Tfd›(in English)

Kosovo (women) News about the team
