\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Larry\_Weinberg\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Larry Weinberg}\label{larry-weinberg}

\begin{itemize}
\item
  \emph{Larry Weinberg (January 23, 1926 -- January 1, 2019) was an
  American real estate developer who was one of the founders of the
  NBA's Portland Trail Blazers.}
\end{itemize}

Larry Weinberg (January 23, 1926 -- January 1, 2019) was an American
real estate developer who was one of the founders of the NBA's Portland
Trail Blazers.

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{Weinberg became president of the Trail Blazers in 1975,
  replacing Sarkowsky, who turned his attention to the NFL's Seattle
  Seahawks.}
\item
  \emph{The Trail Blazers honored Weinberg in 1992 by retiring a \#1
  jersey with his name.}
\item
  \emph{Weinberg wife Barbi was a founder of The Washington Institute
  for Near East Policy, Weinberg died on January 1, 2019 at age 92.}
\end{itemize}

Born to a Jewish family in New York City, Weinberg served in the US 6th
Army Group as an infantryman during World War II. He was severely
wounded in combat in France and spent over a year recovering in a US
military hospital. He attended Cornell University, the University of
Arizona, and the University of California at Los Angeles. In 1948,
Weinberg founded the Larwin Company serving as its CEO until he retired.
By the late 1960s, Larwin Company became one of the largest privately
owned housing companies in the United States until merging it into CNA
Financial Corporation where it became one of the three largest housing
producers with annual development of 8,000 residential units. He went on
to serve as a Member of the Executive Committee and the Board of
Directors of CNA from 1969 to 1980. In 1950, Weinberg founded Com-Air
Products, Inc. which designed, manufactured, and assembled the
hydraulics, pneumatics and fuel assemblies used in jet engines and
aircraft.

In 1970, Weinberg, Herman Sarkowsky, and Robert Schmertz paid \$3.7
million to secure an NBA expansion team for Portland. Weinberg became
president of the Trail Blazers in 1975, replacing Sarkowsky, who turned
his attention to the NFL's Seattle Seahawks. Two years later, the Trail
Blazers won an NBA championship. Weinberg served as team president until
1988, when he sold the team to Paul Allen. The Trail Blazers honored
Weinberg in 1992 by retiring a \#1 jersey with his name. Five players
have since received permission from Weinberg to wear \#1: Rod
Strickland, Derek Anderson, Jarrett Jack, Armon Johnson and Ike Diogu.

In addition to his work in basketball and real estate, Weinberg has
served as president of the American Israel Public Affairs Committee. He
was awarded the Brotherhood Award of the National Conference of
Christians and Jews.

Weinberg wife Barbi was a founder of The Washington Institute for Near
East Policy, Weinberg died on January 1, 2019 at age 92.

\section{Notes}\label{notes}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Learn more about Larry Weinberg from NBA.com}
\end{itemize}

Learn more about Larry Weinberg from NBA.com

Profile at California Building Industry Foundation website
