\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/List\%20of\%20United\%20States\%20Senators\%20from\%20Virginia\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{List of United States Senators from
Virginia}\label{list-of-united-states-senators-from-virginia}

\begin{itemize}
\item
  \emph{Its Senate seats were declared vacant in March 1861, due to its
  secession from the Union, but Senators representing its western
  counties continued to sit until March 1863.}
\item
  \emph{Virginia's Senate seats were again filled from January 1870.}
\end{itemize}

Virginia has sent senators to the U.S. Senate since 1789. Its Senate
seats were declared vacant in March 1861, due to its secession from the
Union, but Senators representing its western counties continued to sit
until March 1863. Virginia's Senate seats were again filled from January
1870. Virginia's current Senators are Democrats Mark Warner and 2016
nominee for Vice President of the United States Tim Kaine.

\section{List of Senators}\label{list-of-senators}

\section{Superlatives (top 5)}\label{superlatives-top-5}

\section{Longest service}\label{longest-service}

\section{Shortest service}\label{shortest-service}

\section{Youngest at beginning of
service}\label{youngest-at-beginning-of-service}

\section{Oldest at end of service}\label{oldest-at-end-of-service}

\section{Living former U.S. Senators from
Virginia}\label{living-former-u.s.-senators-from-virginia}

\begin{itemize}
\item
  \emph{Senators who are currently living, four from Class 1 and one
  from Class 2.}
\item
  \emph{As of January~2019{[}update{]}, there are five former U.S.}
\end{itemize}

As of January~2019{[}update{]}, there are five former U.S. Senators who
are currently living, four from Class 1 and one from Class 2. The most
recent Senator to die was Harry F. Byrd Jr. (served 1965--1983) on July
20, 2013, who is also the most recently serving Senator to die.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{List of United States Representatives from Virginia}
\item
  \emph{United States congressional delegations from Virginia}
\end{itemize}

United States congressional delegations from Virginia

List of United States Representatives from Virginia

\section{References}\label{references}

\begin{itemize}
\item
  \emph{United States Senate Historical Office (volume 4 Bicentennial
  ed.).}
\item
  \emph{Byrd, Robert C. (October 1, 1993).}
\end{itemize}

Byrd, Robert C. (October 1, 1993). Wolff, Wendy (ed.). "The Senate,
1789-1989: Historical Statistics, 1789-1992". United States Senate
Historical Office (volume 4 Bicentennial ed.). Washington, D.C.: U.S.
Government Printing Office.
