\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/List\%20of\%20United\%20States\%20Senators\%20from\%20Indiana\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{List of United States Senators from
Indiana}\label{list-of-united-states-senators-from-indiana}

\begin{itemize}
\item
  \emph{Since then, the state has been represented in the United States
  Senate by 44 different men in Class 1 and 3; David Turpie served
  non-consecutive terms in Class 1, Dan Coats served non-consecutive
  terms in Class 3, and William Ezra Jenner served in both Classes.}
\item
  \emph{Until the passage of the Seventeenth Amendment to the United
  States Constitution in 1913, Senators were elected by the Indiana
  General Assembly; after that they were elected popularly by Indiana
  citizens.}
\item
  \emph{A senatorial term lasts six years beginning on January 3.}
\end{itemize}

Indiana was admitted to the Union on December 11, 1816. Since then, the
state has been represented in the United States Senate by 44 different
men in Class 1 and 3; David Turpie served non-consecutive terms in Class
1, Dan Coats served non-consecutive terms in Class 3, and William Ezra
Jenner served in both Classes. Until the passage of the Seventeenth
Amendment to the United States Constitution in 1913, Senators were
elected by the Indiana General Assembly; after that they were elected
popularly by Indiana citizens. A senatorial term lasts six years
beginning on January 3. In case of a vacancy the Governor of Indiana has
the duty to appoint a new U.S. Senator. The longest-serving of any
Senator from Indiana is Republican Richard Lugar (1977--2013). Indiana's
current U.S. Senators are Republicans Todd Young (serving since 2017)
and Mike Braun (serving since 2019)

\section{List of senators}\label{list-of-senators}

\section{Living former U.S. Senators from
Indiana}\label{living-former-u.s.-senators-from-indiana}

\begin{itemize}
\item
  \emph{Senators from Indiana.}
\end{itemize}

As of April~2019{[}update{]}, there are four living former U.S. Senators
from Indiana. The most recent to die was Richard Lugar (served
1977--2013) on April 28, 2019, who is also the most recently serving to
die.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{United States congressional delegations from Indiana}
\item
  \emph{List of United States Representatives from Indiana}
\end{itemize}

List of United States Representatives from Indiana

United States congressional delegations from Indiana

\section{References and external
links}\label{references-and-external-links}

\begin{itemize}
\item
  \emph{United States Senate Historical Office (volume 4 Bicentennial
  ed.).}
\item
  \emph{Retrieved January 1, 2009.}
\item
  \emph{Senators from Indiana".}
\end{itemize}

"U.S. Senators from Indiana". United States Senate. Retrieved January 1,
2009.

Byrd, Robert C. (October 1, 1993). Wolff, Wendy (ed.). "The Senate,
1789-1989: Historical Statistics, 1789-1992". United States Senate
Historical Office (volume 4 Bicentennial ed.). Washington, DC: U.S.
Government Printing Office.
