\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Lord\%2C\_Give\_Me\_Patience\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Lord, Give Me Patience}\label{lord-give-me-patience}

\begin{itemize}
\item
  \emph{Lord, Give Me Patience (Spanish: Señor, dame paciencia) is a
  2017 Spanish comedy film directed by Álvaro Díaz Lorenzo.}
\end{itemize}

Lord, Give Me Patience (Spanish: Señor, dame paciencia) is a 2017
Spanish comedy film directed by Álvaro Díaz Lorenzo.

\section{Plot}\label{plot}

\begin{itemize}
\item
  \emph{They are joined by Gregorio's other daughter, Alicia, who is
  going out with an anarchic hippy named Leo, and his son Carlos, to
  whom he has not spoken since Carlos announced he was homosexual six
  months ago.}
\item
  \emph{Gregorio's daughter Sandra is married to Jordi, a Catalan and
  diehard Barcelona supporter, who wants to send Gregorio's future
  granddaughter to a bilingual Catalan-English school in Barcelona.}
\end{itemize}

After the sudden death of his wife, Gregorio - a grumpy conservative
Real Madrid fanatic - has to carry out her final wish: to spend a
weekend with his children and their partners in Sanlúcar de Barrameda
and throw her ashes into the Guadalquivir river.

Gregorio's daughter Sandra is married to Jordi, a Catalan and diehard
Barcelona supporter, who wants to send Gregorio's future granddaughter
to a bilingual Catalan-English school in Barcelona.

They are joined by Gregorio's other daughter, Alicia, who is going out
with an anarchic hippy named Leo, and his son Carlos, to whom he has not
spoken since Carlos announced he was homosexual six months ago. Carlos
arrives with his boyfriend Eneko, a Basque of Senegalese origin, far
from the ideal partner Gregorio would have envisioned for his son.

This trip to the south of Spain put this dysfunctional family's capacity
for forgiveness to the test, and sees them forced to accept each other,
warts and all.

\section{Cast}\label{cast}

\begin{itemize}
\item
  \emph{David Guapo as Jordi}
\item
  \emph{Jordi Sánchez as Gregorio}
\end{itemize}

Jordi Sánchez as Gregorio

Rossy de Palma as Maria

Megan Montaner as Sandra

Silvia Alonso as Alicia

Eduardo Casanova as Carlos

David Guapo as Jordi

Andrés Velencoso as Alejandro

Paco Tous as Padre Salcedo

Salva Reina as Leo

Boré Buika as Eneko

Antonio Dechent as Guardia Civil

Jorge Sanz as Hombre after

Alberto Jo Lee as Haruki

Paula Gómez as Carmen

María Cabrera as Pepa

César Oliver as Luis

\section{Reception}\label{reception}

\begin{itemize}
\item
  \emph{Jordi Costa, writing for El País, complained of the film's lack
  of comic timing, and added, "The figure of a policeman, who bellows
  'Gibraltar is Spanish!'}
\item
  \emph{The film was a commercial success in Spain, being the second
  most watched film of the first half of 2017.}
\end{itemize}

The film was a commercial success in Spain, being the second most
watched film of the first half of 2017.

However, it received mixed-to-poor reviews from critics. Jordi Costa,
writing for El País, complained of the film's lack of comic timing, and
added, "The figure of a policeman, who bellows 'Gibraltar is Spanish!'
reflects the type of viewer for this kind of product." ABC gave the film
two stars out of five, criticising the "vulgar metaphor" of using
various characters to reflect "Spain today", but notes that such films
often have more commercial than critical success.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Señor, dame paciencia on IMDb}
\end{itemize}

Señor, dame paciencia on IMDb
