\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Madeleine\_Tabar\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Madeleine Tabar}\label{madeleine-tabar}

\begin{itemize}
\item
  \emph{Tabar was one of the personalities who participated in the
  cultural project "Egypt in the eyes of the world" at the invitation of
  the Embassy of Lebanon in Egypt.}
\item
  \emph{She began her work on radio and television in Lebanon and later
  became a very famous actress in Egypt and the Arab region.}
\item
  \emph{Tabar has worked on television in Egypt.}
\item
  \emph{Madeleine Tabar (Arabic: مادلين طبر) is a Lebanese actress.}
\end{itemize}

Madeleine Tabar (Arabic: مادلين طبر) is a Lebanese actress. She was born
in Beirut. She began her work on radio and television in Lebanon and
later became a very famous actress in Egypt and the Arab region.

Tabar was one of the personalities who participated in the cultural
project "Egypt in the eyes of the world" at the invitation of the
Embassy of Lebanon in Egypt.

Tabar has worked on television in Egypt. She is one of the few actresses
in Egypt who speaks French.

\section{Television series}\label{television-series}

\begin{itemize}
\item
  \emph{Titles translated from Arabic}
\end{itemize}

Titles translated from Arabic

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{The remarks of the Lebanese ambassador about the seminar Egypt
  in the eyes of Lebanon on 26 November 2013 (In Arabic)}
\item
  \emph{The remarks of the Lebanese ambassador about the seminar Egypt
  in the eyes of Lebanon (In Arabic)}
\item
  \emph{Madeleine Tabar on elcinema.com (In Arabic)}
\end{itemize}

The remarks of the Lebanese ambassador about the seminar Egypt in the
eyes of Lebanon on 26 November 2013 (In Arabic)

The remarks of the Lebanese ambassador about the seminar Egypt in the
eyes of Lebanon (In Arabic)

Madeleine Tabar on elcinema.com (In Arabic)
