\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Man\%20in\%20Space\%20Soonest\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Man in Space Soonest}\label{man-in-space-soonest}

\begin{itemize}
\item
  \emph{Another, Neil Armstrong, became a NASA astronaut in 1962 and
  became the first person to walk on the Moon in 1969.}
\item
  \emph{The first, Joseph A. Walker, did so twice in two X-15 rocket
  plane tests in 1963.}
\item
  \emph{Man In Space Soonest (MISS) was a United States Air Force (USAF)
  program to put a man into outer space before the Soviet Union.}
\item
  \emph{Only two men from the program would actually reach outer space.}
\end{itemize}

Man In Space Soonest (MISS) was a United States Air Force (USAF) program
to put a man into outer space before the Soviet Union. The program was
cancelled on August 1, 1958, and was replaced by NASA's Project Mercury.
Only two men from the program would actually reach outer space. The
first, Joseph A. Walker, did so twice in two X-15 rocket plane tests in
1963. Another, Neil Armstrong, became a NASA astronaut in 1962 and
became the first person to walk on the Moon in 1969.

\section{Astronaut candidates}\label{astronaut-candidates}

\begin{itemize}
\item
  \emph{The first member of the group to achieve international astronaut
  recognition, and to enter space twice, on two X-15 test flights.}
\item
  \emph{Flew on Gemini 8 and Apollo 11 missions; performed the first
  docking of two spacecraft, was the first - along with Buzz Aldrin - to
  land on the Moon, and was the first person to set foot on the Moon.}
\end{itemize}

MISS would have used a Thor booster, then later an Atlas, to launch a
single-man spacecraft into orbit. On June 25, 1958, the Air Force
announced the following nine men selected to be astronauts for the
program:

Neil A. Armstrong (1930--2012), 27, NACA. The only member of the group
to join the NASA Astronaut Corps. Flew on Gemini 8 and Apollo 11
missions; performed the first docking of two spacecraft, was the first -
along with Buzz Aldrin - to land on the Moon, and was the first person
to set foot on the Moon.

William B. Bridgeman (1916--1968), 42, Douglas Aircraft Company

A. Scott Crossfield (1921--2006), 36, North American Aviation (NAA)

Iven C. Kincheloe (1928--1958), 29, USAF

John B. McKay (1922--1975), 35, NACA

Robert A. Rushworth (1924--1993), 33, USAF

Joseph A. Walker (1921--1966), 37, NACA. The first member of the group
to achieve international astronaut recognition, and to enter space
twice, on two X-15 test flights.

Alvin S. White (1918--2006), 39, NAA

Robert M. White (1924--2010), 33, USAF

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Vostok Program}
\item
  \emph{Project Mercury}
\end{itemize}

List of astronauts by selection

Project Mercury

Vostok Program

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{"First Up?}
\item
  \emph{", Tony Reichhardt, Air \& Space Magazine, August/September
  2000.}
\end{itemize}

Encyclopedia Astronautica entry.

"First Up?", Tony Reichhardt, Air \& Space Magazine, August/September
2000.
