\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Matt\_Brown\_\%28Canadian\_politician\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Matt Brown (Canadian
politician)}\label{matt-brown-canadian-politician}

\begin{itemize}
\item
  \emph{Matthew Brown is a Canadian politician, who was elected mayor of
  London, Ontario in the city's 2014 municipal election.}
\end{itemize}

Matthew Brown is a Canadian politician, who was elected mayor of London,
Ontario in the city's 2014 municipal election.

\section{Background}\label{background}

\begin{itemize}
\item
  \emph{Brown was born in London, he grew up in Woodstock before
  graduating from the University of Waterloo.}
\end{itemize}

Brown was born in London, he grew up in Woodstock before graduating from
the University of Waterloo. He has two sons.

\section{Mayoralty}\label{mayoralty}

\begin{itemize}
\item
  \emph{Prior to his election to the mayoralty, Brown represented Ward 7
  on London City Council.}
\end{itemize}

In the 2014 mayoral race, he defeated runner up Paul Cheng. Prior to his
election to the mayoralty, Brown represented Ward 7 on London City
Council.

In a 2017 episode of the television series Political Blind Date, Brown
and Giorgio Mammoliti discussed their differing perspectives on the
issue of safe injection sites.

In April 2018 Brown announced that he would not seek re-election in the
upcoming municipal election.

\section{Affair}\label{affair}

\begin{itemize}
\item
  \emph{Brown announced his return to duties as mayor on June 22, 2016
  and on June 23, 2016 attended his first council meeting since the
  leave.}
\item
  \emph{On June 14, 2016, he temporarily suspended his duties as mayor
  following his disclosure of an affair with deputy mayor Maureen
  Cassidy.}
\item
  \emph{The London Integrity Commissioner issued a report to City
  Council stating that Matt Brown and Maureen Cassidy violated sections
  2.4, 5.1 and 5.1(1)(e) of the Municipal Code of Conduct.}
\end{itemize}

On June 14, 2016, he temporarily suspended his duties as mayor following
his disclosure of an affair with deputy mayor Maureen Cassidy. The
affair drew national attention across Canada. The London Integrity
Commissioner issued a report to City Council stating that Matt Brown and
Maureen Cassidy violated sections 2.4, 5.1 and 5.1(1)(e) of the
Municipal Code of Conduct. In the report the integrity commissioner
stated that he "has no authority" under current guidelines, to demand a
resignation or prevent either office holder from running for
re-election.

Brown announced his return to duties as mayor on June 22, 2016 and on
June 23, 2016 attended his first council meeting since the leave.

On September 29, 2016 it was announced by CBC News that he had separated
from his wife, Andrea.

\section{Electoral record}\label{electoral-record}

\section{2010 Ward 7 race}\label{ward-7-race}

\section{2014 mayoral race}\label{mayoral-race}

\begin{itemize}
\item
  \emph{\\
  Ali Hamadi\\
  7\\
  0.01}
\end{itemize}

Ali Hamadi\\
7\\
0.01

\section{References}\label{references}
