\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Mediaite\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Mediaite}\label{mediaite}

\begin{itemize}
\item
  \emph{Mediaite is a digital news site that covers political news
  through the eyes of mainstream media.}
\item
  \emph{Part of the Abrams Media Network and founded by Dan Abrams,
  Mediaite covers breaking news, offers opinions, and analysis across
  the political spectrum including reporting on top media moments from
  cable news channels like CNN, FOX, MSNBC, CNBC, \& more.}
\end{itemize}

Mediaite is a digital news site that covers political news through the
eyes of mainstream media. Part of the Abrams Media Network and founded
by Dan Abrams, Mediaite covers breaking news, offers opinions, and
analysis across the political spectrum including reporting on top media
moments from cable news channels like CNN, FOX, MSNBC, CNBC, \& more.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{By early 2010, Mediaite launched a more aggressive strategy for
  covering cable news segments, which became the progenitor for many
  media and political websites today.}
\item
  \emph{At launch, Mediaite's `Power Grid' drew attention for weekly
  rankings of various media figures across various platforms based on
  data-driven metrics such as Google News mentions, Twitter followers,
  TV ratings, Circulation and mentions on TV transcripts.}
\item
  \emph{For the month of January 2017, Dan Abrams revealed that Mediaite
  reached 11.86 million unique visitors.}
\end{itemize}

Mediaite launched in July 2009 with Founding Editor Colby Hall alongside
an editorial staff that included Rachel Sklar, Glynnis MacNicol and
Steve Krakauer. At launch, Mediaite's `Power Grid' drew attention for
weekly rankings of various media figures across various platforms based
on data-driven metrics such as Google News mentions, Twitter followers,
TV ratings, Circulation and mentions on TV transcripts.

By early 2010, Mediaite launched a more aggressive strategy for covering
cable news segments, which became the progenitor for many media and
political websites today.

For the month of January 2017, Dan Abrams revealed that Mediaite reached
11.86 million unique visitors.

Mediaite's writers have included Noah Rothman, Philip Bump, Joe Concha,
Tina Nguyen and many other well known reporters.

\section{Mediaite's Most Influential In News
Media}\label{mediaites-most-influential-in-news-media}

\begin{itemize}
\item
  \emph{Mediaite's Most Influential - 2015}
\item
  \emph{Mediaite's Most Influential - 2016}
\item
  \emph{Mediaite's Most Influential - 2017}
\item
  \emph{Every December, Mediaite publishes a list of the 75 most
  influential people in news media---compiled by all of the Mediaite
  editors.}
\item
  \emph{Mediaite's Most Influential - 2018}
\end{itemize}

Every December, Mediaite publishes a list of the 75 most influential
people in news media---compiled by all of the Mediaite editors. The
publication of the list culminates in a party hosted by the site and
attended by many top cable anchors and correspondents. The list is in
its 4th year.

Mediaite's Most Influential - 2015

Mediaite's Most Influential - 2016

Mediaite's Most Influential - 2017

Mediaite's Most Influential - 2018

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Official website}
\end{itemize}

Official website
