\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/MESUR\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{MESUR}\label{mesur}

\begin{itemize}
\item
  \emph{The only mission of the program that was completed was MESUR
  Pathfinder.}
\item
  \emph{MESUR, the Mars Environmental SURvey was a NASA program designed
  to explore the planet Mars in preparation for human follow-up missions
  of the Space Exploration Initiative.}
\end{itemize}

MESUR, the Mars Environmental SURvey was a NASA program designed to
explore the planet Mars in preparation for human follow-up missions of
the Space Exploration Initiative. The only mission of the program that
was completed was MESUR Pathfinder.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{They were planned to be low-cost missions to Mars, instead of
  multibillion-dollar missions.}
\item
  \emph{MESUR was a planned set of 16 surface missions on Mars that
  would also set up a planetary network across Mars and work in
  conjunction with Mars Observer.}
\item
  \emph{After the loss of Mars Observer, the MESUR program was shelved,
  and Pathfinder became part of the NASA Discovery Program.}
\end{itemize}

MESUR was a planned set of 16 surface missions on Mars that would also
set up a planetary network across Mars and work in conjunction with Mars
Observer.{[}dead link{]} The original plan was proposed by NASA Ames,
but it would eventually include ideas from the competing JPL proposal.
It was envisioned as a low-cost method of surveying Mars, with risk
tolerance, since a loss of a spacecraft was not fatal to the program,
because of multiple relatively cheap space probes.

MESUR Pathfinder would be the pathfinder mission for the MESUR program.
MESUR regular missions would start landing in 1999. The multi-year MESUR
would have 16 more landers, landing in the projected period of
1999-2003,{[}dead link{]} and lasting 10 years. Launches would start in
1996.{[}dead link{]} Several of the landers would carry Sojourner-class
rovers.{[}dead link{]} The entire program was projected at a cost of \$1
billion US, with per annum spending restricted to \$150 million US,
starting in FY1994. They were planned to be low-cost missions to Mars,
instead of multibillion-dollar missions.

The rovers and landers would have instruments and cameras to examine
surface rocks, search for water, perform seismography, and observe
meteorology. The seismology experiments would help determine the
internal structure of Mars.

After Pathfinder, in 1999, four landers would be launched in a single
rocket. At the next launch window in 2001, four more landers would again
launch in on a single rocket. Finally in 2003, the last eight landers
would launch on two rockets.

On 26 June 1992, NASA unveiled the prototype for Mars Sojourner, Rocky
IV, on the 25th anniversary of the first US lunar lander.

After the loss of Mars Observer, the MESUR program was shelved, and
Pathfinder became part of the NASA Discovery Program.{[}dead link{]}

\section{Missions}\label{missions}

\section{MESUR Pathfinder}\label{mesur-pathfinder}

\begin{itemize}
\item
  \emph{The MESUR Pathfinder was launched on December 4, 1996 by NASA
  aboard a Delta II.}
\item
  \emph{After a 7-month voyage it landed on Ares Vallis, in a region
  called Chryse Planitia on Mars, on 4 July 1997.}
\item
  \emph{After the landing, the Mars Pathfinder was renamed as the Sagan
  Memorial Station in honor of the famous astronomer and planetologist
  Carl Sagan.}
\end{itemize}

The MESUR Pathfinder was launched on December 4, 1996 by NASA aboard a
Delta II. After a 7-month voyage it landed on Ares Vallis, in a region
called Chryse Planitia on Mars, on 4 July 1997. During its voyage the
spacecraft had to accomplish four flight adjustments on 10 January, 3
February, 6 May and 25 June. The lander opened, exposing the rover
called Sojourner that would go on to execute many experiments on the
Martian surface.

Although the mission was programmed to last a week to a month, it
eventually lasted for almost three months. The final contact with the
Pathfinder was at 10:23 UTC on September 27, 1997. Although the mission
planners tried to restore contact during the following five months, the
successful mission was terminated on March 10, 1998. After the landing,
the Mars Pathfinder was renamed as the Sagan Memorial Station in honor
of the famous astronomer and planetologist Carl Sagan. The mission had
exceeded its goals in the first month.

\section{References}\label{references}
