\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Michael\%20Kranish\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Michael Kranish}\label{michael-kranish}

\begin{itemize}
\item
  \emph{He joined The Washington Post in 2015, where he is an
  investigative political reporter.}
\item
  \emph{Michael Kranish (born 1957) is an American author and former
  correspondent with The Boston Globe.}
\end{itemize}

Michael Kranish (born 1957) is an American author and former
correspondent with The Boston Globe. He joined The Washington Post in
2015, where he is an investigative political reporter.

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{His other assignments with the Globe have included congressional
  reporter, New England reporter, and business writer.}
\item
  \emph{A graduate of the Maxwell School of Citizenship and Public
  Affairs at Syracuse University, Michael Kranish joined the Globe in
  1984.}
\item
  \emph{He is co-author with Globe writer Scott Helman of The Real
  Romney.}
\end{itemize}

A graduate of the Maxwell School of Citizenship and Public Affairs at
Syracuse University, Michael Kranish joined the Globe in 1984. Since
1990 he has worked in the newspaper's Washington Bureau and was the
White House reporter during the last two years of the presidency of
George H.W. Bush and the first two years of Bill Clinton. He was the
paper's national political reporter during the 1996 and 2000 campaigns.
His other assignments with the Globe have included congressional
reporter, New England reporter, and business writer. He previously
worked for the Miami Herald and the Lakeland Ledger.{[}citation
needed{]}

He is the co-author (with Brian C. Mooney, and Nina J. Easton) of a
biography of Senator John Kerry, John F. Kerry: The Complete Biography
by the Boston Globe Reporters Who Know Him Best, and the author of a
history of Thomas Jefferson, Flight from Monticello: Thomas Jefferson at
War. He is co-author with Globe writer Scott Helman of The Real Romney.

With co-author Marc Fisher and supervised by The Washington Post editor
Marty Baron, Kranish authored the biography, Trump Revealed: An American
Journey of Ambition, Ego, Money, and Power.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Interview with Kranish on "New Books in Biography"}
\item
  \emph{Flight from Monticello: Thomas Jefferson at War at OUP}
\end{itemize}

Appearances on C-SPAN

Flight from Monticello: Thomas Jefferson at War at OUP

Interview with Kranish on "New Books in Biography"
