\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Mr.\_Telephone\_Man\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Mr. Telephone Man}\label{mr.-telephone-man}

\begin{itemize}
\item
  \emph{"Mr. Telephone Man" is a song by New Edition, and the second
  single from their eponymous second album, New Edition.}
\end{itemize}

"Mr. Telephone Man" is a song by New Edition, and the second single from
their eponymous second album, New Edition. Released as a single, by
December 8, 1984, it was being added to the most "Hot Black" radio
station playlists.

\section{Overview}\label{overview}

\begin{itemize}
\item
  \emph{The single reached number 12 on the Billboard Hot 100 singles
  chart and was the group's third number-one single on the Black Singles
  chart.}
\item
  \emph{Parker produced the original version as well as the cover by New
  Edition.}
\end{itemize}

"Mr. Telephone Man" included lead vocals from Ralph Tresvant, Ricky Bell
and Bobby Brown with a rap by Michael Bivins and was written by Ray
Parker Jr. The song was originally recorded by teenage singer Junior
Tucker, who included the song on his self-titled debut album on Geffen
Records in 1983. Parker produced the original version as well as the
cover by New Edition.

The single reached number 12 on the Billboard Hot 100 singles chart and
was the group's third number-one single on the Black Singles chart.
Mixes included the instrumental and the "Extended Version".

\section{Track listing}\label{track-listing}

\begin{itemize}
\item
  \emph{Mr. Telephone Man (Extended Version) -- 6:30}
\item
  \emph{Mr. Telephone Man (Instrumental) -- 5:40}
\end{itemize}

1. Mr. Telephone Man (Extended Version) -- 6:30

2. Mr. Telephone Man (Instrumental) -- 5:40

\section{Personnel}\label{personnel}

\begin{itemize}
\item
  \emph{Bobby Brown -- lead and background vocals}
\item
  \emph{Ralph Tresvant -- lead and background vocals}
\item
  \emph{Michael Bivins -- background vocals, rap}
\item
  \emph{Ricky Bell -- lead and background vocals}
\item
  \emph{Ronnie DeVoe -- background vocals}
\end{itemize}

Engineer -- Taavi Mote

Executive Producer -- Jheryl Busby

Producer -- Ray Parker Jr.

Remix -- Louil Silas Jr.

Ronnie DeVoe -- background vocals

Bobby Brown -- lead and background vocals

Ricky Bell -- lead and background vocals

Michael Bivins -- background vocals, rap

Ralph Tresvant -- lead and background vocals

Jack Ashford -- tambourine

Sylvester Rivers -- electric piano

Sonny Burke -- piano

\section{Chart performance}\label{chart-performance}

\section{Weekly charts}\label{weekly-charts}

\section{Year-end charts}\label{year-end-charts}

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{List of number-one R\&B singles of 1985 (U.S.)}
\end{itemize}

List of number-one R\&B singles of 1985 (U.S.)

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{New Edition - Mr. Telephone Man on YouTube}
\end{itemize}

Lyrics of this song at MetroLyrics

New Edition - Mr. Telephone Man on YouTube
