\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/NASA\%20Social\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{NASA Social}\label{nasa-social}

\begin{itemize}
\item
  \emph{Many NASA Social events are at least partially broadcast on NASA
  TV and UStream.}
\item
  \emph{NASA has hosted many events for its social media enthusiasts
  called NASA Socials (formerly NASA Tweetups) beginning in 2009.}
\item
  \emph{As of 2015, all NASA field centers and NASA Headquarters have
  hosted NASA Tweetup/Social events.}
\end{itemize}

NASA has hosted many events for its social media enthusiasts called NASA
Socials (formerly NASA Tweetups) beginning in 2009. These events are
targeted at the social media followers of NASA through platforms such as
Twitter, Facebook, Google Plus, Instagram, YouTube and more. They
provide guests with VIP access to NASA facilities and speakers with the
goal of leveraging participants' social networks to further the outreach
requirements of NASA as laid out in the National Aeronautics and Space
Act. NASA re-branded these events as "Socials" in March 2012 as it
expanded participation to services beyond just Twitter.

As of 2015, all NASA field centers and NASA Headquarters have hosted
NASA Tweetup/Social events. There were 5 NASA Tweetups in 2009, 10 in
2010, 16 in 2011, 21 in 2012, 22 in 2013, and 23 in 2014. In August
2011, over 2,000 participants had been part of official NASA Tweetups.
By July 2014, that number had swelled to over 6,000 total participants
in over 5 years of NASA Social programs.

Many NASA Social events are at least partially broadcast on NASA TV and
UStream. NASA Socials are held at NASA centers, NASA Headquarters,
observatories, engine test sites, museums such as the Newseum and
National Air and Space Museum, and during larger events such as SXSW and
World Space Week. The length of socials range from a few hours to a
couple days to much longer in the case of some events, such as the
STS-133 launch tweetup.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{In an attempt to measure the impact of tweetups, NASA tracked
  10,665 tweets originating from 150 participants in the August 2011
  Juno Tweetup as well as the subsequent retweets and found 29.9 million
  potential impressions.}
\item
  \emph{The first NASA Tweetup was held at the Jet Propulsion Laboratory
  in Pasadena, California, in January 2009.}
\end{itemize}

The first NASA Tweetup was held at the Jet Propulsion Laboratory in
Pasadena, California, in January 2009. During this event, guests were
given exclusive tours and access to JPL scientists and
engineers.\textbar{}

In an attempt to measure the impact of tweetups, NASA tracked 10,665
tweets originating from 150 participants in the August 2011 Juno Tweetup
as well as the subsequent retweets and found 29.9 million potential
impressions.

\section{Speakers and participants}\label{speakers-and-participants}

\begin{itemize}
\item
  \emph{Speakers at NASA tweetup/social events have included NASA
  engineers, scientists, executives and well over 80 NASA astronauts.}
\end{itemize}

Speakers at NASA tweetup/social events have included NASA engineers,
scientists, executives and well over 80 NASA astronauts. Notable
speakers include NASA Administrator Charles Bolden, SpaceX President
Gwynne Shotwell, Senator and astronaut John Glenn, Bill Nye, and final
Space Shuttle crew members Sandy Magnus and Chris Ferguson.{[}citation
needed{]}

While the majority of participants in NASA tweetups/socials have been
space enthusiasts, there have also been many "celebrity" participants,
including Neil deGrasse Tyson, LeVar Burton, Trey Ratcliff, Robert
Scoble, Bill Prady, Kevin Clash, Miles O'Brien, Seth Green, will.i.am,
and many others.{[}citation needed{]}

\section{List of NASA Socials \&
Tweetups}\label{list-of-nasa-socials-tweetups}

\section{Awards}\label{awards}

\begin{itemize}
\item
  \emph{NASA Exceptional Service Medal}
\item
  \emph{NASA Group Achievement Award}
\item
  \emph{2012 Shorty Awards for best social media manager to NASA's
  Stephanie Schierholz}
\item
  \emph{2012 \& 2013 Shorty Awards for best government use of social
  media.}
\end{itemize}

2009 Shorty Awards for science for updates on the Mars Phoenix Lander

Space Foundation's 2012 Douglas S. Morrow Public Outreach Award

2012 Shorty Awards for best social media manager to NASA's Stephanie
Schierholz

2012 \& 2013 Shorty Awards for best government use of social media.

Space Flight Awareness Award

NASA Exceptional Service Medal

NASA Group Achievement Award

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{NASA on Twitter}
\item
  \emph{Official site for NASA Socials}
\end{itemize}

Official site for NASA Socials

NASASocial on Twitter

NASA on Twitter

TweetupSpace on Twitter

9.88 gigapixel panoramic image of Juno Tweetup

\section{References}\label{references}
