\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Outsider\%20in\%20the\%20White\%20House\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Outsider in the White House}\label{outsider-in-the-white-house}

\begin{itemize}
\item
  \emph{It was first published as Outsider in the House in 1997.}
\item
  \emph{Outsider in the White House is a 2015 political memoir
  co-authored by Huck Gutman and presidential candidate Bernie Sanders,
  with an afterword by journalist John Nichols.}
\end{itemize}

Outsider in the White House is a 2015 political memoir co-authored by
Huck Gutman and presidential candidate Bernie Sanders, with an afterword
by journalist John Nichols. It was first published as Outsider in the
House in 1997.

\section{Content}\label{content}

\begin{itemize}
\item
  \emph{In fact, to the British reviewer, Bernie Sanders sounds just
  like Jeremy Corbyn, unsurprising given that both men are lifelong
  socialists.}
\item
  \emph{The 2015 reedition argues that the Republican Revolution remains
  relevant because "for Sanders, the only thing that's changed over the
  past 20 years is that the bad guys have got worse".}
\end{itemize}

A review in the British magazine Prospect finds Outsider surprisingly au
courant for a reprint of a 20-year-old book, asserting that once readers
get past the focus on Newt Gingrich era politics, the issues Sanders was
addressing in the 90s: the negative impact of free trade on American
wages, income inequality, falling working class wages, military
overspending, poverty, and the negative impact of big corporation, feel
contemporary. In fact, to the British reviewer, Bernie Sanders sounds
just like Jeremy Corbyn, unsurprising given that both men are lifelong
socialists.

The book talks about Sanders's support for the Second Amendment to the
United States Constitution, which gives United States citizens the right
to bear arms.

Additionally, the book talks about the Republican Revolution spearheaded
by Newt Gingrich. Sanders adds that the Republican Revolution works hand
in hand with the Christian Coalition, whose main focus is on "immigrant
and gay bashing". The 2015 reedition argues that the Republican
Revolution remains relevant because "for Sanders, the only thing that's
changed over the past 20 years is that the bad guys have got worse".

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Presentation on C-Span}
\end{itemize}

Presentation on C-Span
