\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Pamela\%20Brown\%20\%28journalist\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Pamela Brown (journalist)}\label{pamela-brown-journalist}

\begin{itemize}
\item
  \emph{Pamela Ashley Brown (born November 29, 1983) is an American
  television reporter and newscaster.}
\item
  \emph{Brown works as Justice Correspondent for CNN.}
\end{itemize}

Pamela Ashley Brown (born November 29, 1983) is an American television
reporter and newscaster. Brown works as Justice Correspondent for CNN.
She formerly worked for ABC Washington, D.C., affiliate WJLA-TV. Brown
occasionally provided the lead-in to "Politico's Video Playback"---a
daily recap of the previous night's U.S. late-night talk shows.

\section{Biography}\label{biography}

\begin{itemize}
\item
  \emph{Brown Sr. and the half-sister of former Kentucky Secretary of
  State John Y.}
\item
  \emph{Brown, III.}
\item
  \emph{Brown was born in Lexington, Kentucky, the daughter of
  businessman and former Governor of Kentucky John Y.}
\item
  \emph{Brown Jr. and former Miss America and businesswoman Phyllis
  George.}
\item
  \emph{While at the University of North Carolina, Brown was a reporter
  on the university's Carolina Week.}
\end{itemize}

Brown was born in Lexington, Kentucky, the daughter of businessman and
former Governor of Kentucky John Y. Brown Jr. and former Miss America
and businesswoman Phyllis George. George took maternity leave from her
duties on CBS' NFL pregame show, The NFL Today, to give birth to Pamela.
She is also the granddaughter of politician John Y. Brown Sr. and the
half-sister of former Kentucky Secretary of State John Y. Brown, III.
Her parents divorced in 1996 when Brown was 13 after 17 years of
marriage.

Brown graduated from Henry Clay High School in Lexington and the
University of North Carolina at Chapel Hill with a degree in broadcast
journalism. While at the University of North Carolina, Brown was a
reporter on the university's Carolina Week. After school, she worked for
ABC-affiliate WJLA-TV in Washington.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{Brown and Wright had their wedding on June 5, 2017.}
\item
  \emph{Brown became engaged to her boyfriend Adam Wright.}
\item
  \emph{Brown was named after her aunt, Pamela Brown, who died in 1970
  at the age of 28, along with her husband Rod Anderson and balloonist
  Malcolm Brighton, in an ill-fated attempt to cross the Atlantic Ocean
  in a Rozière balloon Free Life.}
\end{itemize}

Brown has an older brother, Lincoln (born 1980) and three half-siblings
from her father's prior marriage. Brown was named after her aunt, Pamela
Brown, who died in 1970 at the age of 28, along with her husband Rod
Anderson and balloonist Malcolm Brighton, in an ill-fated attempt to
cross the Atlantic Ocean in a Rozière balloon Free Life.

Brown became engaged to her boyfriend Adam Wright. Brown and Wright had
their wedding on June 5, 2017. In June 2018 their son Ben was born .

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Pamela Brown's biography on WJLA's website.}
\item
  \emph{Profile of Pamela Brown in Washington Post, September 18, 2006}
\item
  \emph{Pamela Brown's biography on CNN's website.}
\end{itemize}

Pamela Brown's biography on CNN's website.

Pamela Brown's biography on WJLA's website.

Profile of Pamela Brown in Washington Post, September 18, 2006
