\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Riccardo\_Fraccari\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Riccardo Fraccari}\label{riccardo-fraccari}

\begin{itemize}
\item
  \emph{Fraccari has expanded international baseball properties to
  include a new flagship world tournament, the WBSC Premier 12
  Professional Baseball National Team Championship, and also the
  Under-12 Baseball World Cup and the Under-21 Baseball World Cup, which
  impact baseball's World Rankings.}
\item
  \emph{In August 2016 under Fraccari, the International Olympic
  Committee voted to reinstate baseball and softball as Olympic sports
  for the Tokyo 2020 Games.}
\end{itemize}

Riccardo Fraccari (born 30 May 1949 in Pisa, Italy) is a world sport
administrator, holding various high-ranking positions, most notably as
president of the World Baseball Softball Confederation and International
Baseball Federation. In August 2016 under Fraccari, the International
Olympic Committee voted to reinstate baseball and softball as Olympic
sports for the Tokyo 2020 Games. He was elected WBSC president in May
2014, and is serving a 7-year term.

Fraccari was elected as president of the International Baseball
Federation in December 2009, succeeding American Harvey Schiller, and
immediately set out to hold merger discussions with the International
Softball Federation. He spearheaded negotiations to consolidate
international baseball and softball to establish and successfully launch
the World Baseball Softball Confederation in October 2012, uniting
baseball and softball's global movements and streamlining the two
sports' efforts to return to the Olympic Games.

In February 2015, Fraccari appointed Antonio Castro, the son of former
Cuban leader Fidel Castro, as WBSC Global Ambassador and Kenyon \&
Kenyon Washington D.C.-based attorney Edward Colbert, brother of
American political satirist Stephen Colbert, as WBSC General Counsel.

In less than three years since overseeing the establishment of the WBSC,
Fraccari has elevated the new world ruling body to be considered among
the Top 30 "Ultimate Sports Federations" in the world.

Fraccari has expanded international baseball properties to include a new
flagship world tournament, the WBSC Premier 12 Professional Baseball
National Team Championship, and also the Under-12 Baseball World Cup and
the Under-21 Baseball World Cup, which impact baseball's World Rankings.

Under Fraccari, the world governing body for baseball also established
the first-ever "Europe" team to compete in officially recognized
international competitions, setting a historical precedent.

Fraccari also serves as the current chairman of the Italian National
Olympic Committee's (CONI) International Relations Exploratory Committee
and is a member of the CONI Council. He was appointed a member of CONI's
highest authoritative body, the Executive Board ("Giunta"), in August
2018.

In May 2013, Fraccari was elected as the Secretary General of the
Association of IOC Recognised International Sports Federations.

In April 2018, Bulgaria's National Sports Academy of Sofia named
Fraccari an Honorary Professor.

In May 2018, the WBSC under Fraccari established Baseball5, a new
street/urban baseball discipline that only requires a ball.

Fraccari is also an advisory board member of the global sports think
tank, Doha GOALS.

Fraccari is fluent in English, French, Italian and Spanish.

\section{Education}\label{education}

\begin{itemize}
\item
  \emph{Fraccari is a retired professor of organic chemistry at the
  Livorno Technical Institute (Istituto Tecnico Industriale "Galileo
  Galilei") and also studied law at the University of Pisa.}
\end{itemize}

Fraccari is a retired professor of organic chemistry at the Livorno
Technical Institute (Istituto Tecnico Industriale "Galileo Galilei") and
also studied law at the University of Pisa.

\section{Honours and decorations}\label{honours-and-decorations}

\begin{itemize}
\item
  \emph{~Bulgaria~: Honorary Professor, Bulgaria National Sports
  Academy}
\item
  \emph{~Bulgaria~: Title Honoris Causa of Bulgaria}
\item
  \emph{~Italy~: Knight of Merit of the Italian Republic}
\item
  \emph{~Italy~: Italian National Olympic Committee "Gold Star of Sport
  Merit"}
\end{itemize}

~Italy~: Knight of Merit of the Italian Republic

~Italy~: Italian National Olympic Committee "Gold Star of Sport Merit"

~Bulgaria~: Honorary Professor, Bulgaria National Sports Academy

~Bulgaria~: Title Honoris Causa of Bulgaria

\section{Personal}\label{personal}

\begin{itemize}
\item
  \emph{Fraccari is married to a Swiss national; the couple have one son
  who graduated in law from LUISS "Guido Carli" University in Rome.}
\item
  \emph{Fraccari splits his residence between Livorno and Rome, Italy.}
\end{itemize}

Fraccari is married to a Swiss national; the couple have one son who
graduated in law from LUISS "Guido Carli" University in Rome. Fraccari
splits his residence between Livorno and Rome, Italy.

\section{References}\label{references}
