\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Richard\%20Winger\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Richard Winger}\label{richard-winger}

\begin{itemize}
\item
  \emph{Since 1985 Winger has published Ballot Access News,\\
  a monthly newsletter covering developments in ballot access law and
  among the minor parties generally.}
\item
  \emph{He is the publisher and editor of Ballot Access News.}
\item
  \emph{Winger publishes analysis, statistics and legal information and
  supports more equitable laws allowing access to the ballot for minor
  parties.}
\item
  \emph{Winger is widely regarded as an expert on ballot access and
  election law.}
\end{itemize}

Richard Lee Winger (born August 27, 1943) is an American political
activist and analyst. He is the publisher and editor of Ballot Access
News. He sits on the editorial board of the Election Law Journal. Winger
publishes analysis, statistics and legal information and supports more
equitable laws allowing access to the ballot for minor parties.

Winger is widely regarded as an expert on ballot access and election
law.\\
Though not a lawyer, he testifies in court cases and legislative
hearings and is a source for media and political organizers. He has been
published in The Wall Street Journal, Journal of Election Law, the
Fordham Urban Law Review, American Review of Politics, California
Journal and other publications. He has appeared as a commentator on
ballot access on NBC, ABC, CNN, and NPR. Since 1985 Winger has published
Ballot Access News,\\
a monthly newsletter covering developments in ballot access law and
among the minor parties generally.

\section{Background}\label{background}

\begin{itemize}
\item
  \emph{A lifelong Californian, Richard Winger graduated from the
  University of California, Berkeley as a Political Science major in
  1966, and attended Graduate School in Political Science at UCLA.}
\end{itemize}

A lifelong Californian, Richard Winger graduated from the University of
California, Berkeley as a Political Science major in 1966, and attended
Graduate School in Political Science at UCLA.

\section{Coalition on Free and Open
Elections}\label{coalition-on-free-and-open-elections}

\begin{itemize}
\item
  \emph{In 1985 Winger helped found, along with several minor party
  representatives, the Coalition on Free and Open Elections (COFOE).}
\item
  \emph{The group attempts to co-ordinate action and provide mutual
  support among the various minor parties for efforts to liberalize and
  reform ballot access laws.}
\end{itemize}

In 1985 Winger helped found, along with several minor party
representatives, the Coalition on Free and Open Elections (COFOE). The
group attempts to co-ordinate action and provide mutual support among
the various minor parties for efforts to liberalize and reform ballot
access laws.

\section{Politics}\label{politics}

\begin{itemize}
\item
  \emph{Winger finished fourth among five candidates with 1.5\% of the
  vote.}
\item
  \emph{Winger has made one run for public office, a 1986 campaign for
  Secretary of State of California on the Libertarian ballot line.}
\item
  \emph{Winger has been a member of the Libertarian Party for several
  years.}
\end{itemize}

Winger has been a member of the Libertarian Party for several years.

Winger has made one run for public office, a 1986 campaign for Secretary
of State of California on the Libertarian ballot line. As he was running
for the office charged with the administration of elections, the
campaign was styled as being nonpartisan, intended to represent the
interests of all minor parties. Winger finished fourth among five
candidates with 1.5\% of the vote.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Ballot Access News}
\end{itemize}

Ballot Access News

COFOE

Appearances on C-SPAN
