\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Sam\%20Seder\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Sam Seder}\label{sam-seder}

\begin{itemize}
\item
  \emph{Since 2010 he has hosted a daily political talk show, The
  Majority Report with Sam Seder.}
\item
  \emph{Samuel Lincoln Seder (born November 28, 1966) is an American
  comedian, writer, actor, film director, television producer, and
  politically progressive talk radio host.}
\end{itemize}

Samuel Lincoln Seder (born November 28, 1966) is an American comedian,
writer, actor, film director, television producer, and politically
progressive talk radio host. His works include the film Who's the
Caboose? (1997) starring Sarah Silverman and Seder as well as the
television shows Beat Cops (2001) and Pilot Season (2004), a spinoff of
his independent film with Silverman that was originally broadcast on the
now-defunct Trio cable network. He also appeared in Next Stop Wonderland
(1998) and made guest appearances on Spin City (1997), Sex and the City
(2000), America Undercover (2005), and Maron (2015). Since 2010 he has
hosted a daily political talk show, The Majority Report with Sam Seder.
He also voices a recurring antagonistic character, Hugo, on the animated
comedy series Bob's Burgers.

\section{Early life}\label{early-life}

\begin{itemize}
\item
  \emph{Seder was born to a Jewish family in New York City, and was
  raised in Worcester, Massachusetts.}
\end{itemize}

Seder was born to a Jewish family in New York City, and was raised in
Worcester, Massachusetts.

\section{Career}\label{career}

\begin{itemize}
\item
  \emph{Seder was relegated to a Sunday show entitled Seder on Sunday.}
\item
  \emph{Air America Media cancelled Breakroom Live with Maron \& Seder
  in July 2009.}
\item
  \emph{Air America later renewed Seder's contract, giving him top
  billing and retooling the program as The Sam Seder Show.}
\item
  \emph{Seder also works as a periodic political contributor for MSNBC.}
\item
  \emph{The final Seder on Sunday was broadcast on June 1, 2008.}
\end{itemize}

Seder currently works, or has worked, for multiple liberal and
progressive networks/programs throughout the course of his career. In
March 2004, Seder became co-host of Air America Radio's The Majority
Report alongside Janeane Garofalo.

Air America later renewed Seder's contract, giving him top billing and
retooling the program as The Sam Seder Show. The show was also moved to
a time slot with higher viewership traffic.{[}citation needed{]}

As part of Air America President Mark J. Green's restructuring plan to
transform Air America into a profitable leader in progressive talk
radio, called "Air America 2.0", The Sam Seder Show was cancelled on
April 13, 2007 and replaced by WOR Radio Network late night radio show
host Lionel. Seder was relegated to a Sunday show entitled Seder on
Sunday. The plan immediately backfired. Lionel lost two-thirds of
Seder's live affiliates, live streaming and most of the audience within
a year of assuming the timeslot. The final Seder on Sunday was broadcast
on June 1, 2008.{[}citation needed{]}

Seder also occasionally substituted for Randi Rhodes when Rhodes was on
Air America (becoming the number one sub after KLSD morning host Stacy
Taylor lost his job when the station changed its format), as well as
Mike Malloy on The Mike Malloy Show on the Nova M Radio network. In 2008
he also began a collaboration with Marc Maron on Maron v. Seder, an
hour-long video webcast. In January 2009, Maron v. Seder was renamed
Breakroom Live with Maron \& Seder and aired live from the kitchen in
the Air America offices weekdays at 3PM Eastern. Seder and Maron also
hosted a post-show chat with viewers after each episode. Air America
Media cancelled Breakroom Live with Maron \& Seder in July 2009.

In November 2009 Seder hosted a pilot for NBC of an American version of
Have I Got News For You. Three years later, in November 2012, it was
announced Seder would again be the host of an American version of the
show, this time on TBS.

In November 2010, Seder began an independent online podcast, also called
The Majority Report. The live talk-show format closely matches the
previous Air America program, with politically oriented commentary by
Seder and co-hosts and interviews with various guests. Seder offers
listeners different tiered levels of access to content around the show
via crowdfunding platform Patreon.

In late 2010, Seder began occasionally serving as substitute host of
Countdown with Keith Olbermann when Olbermann was on vacation. In
December 2010, Seder also became co-host of the nationally syndicated
progressive radio interview program Ring of Fire, co-hosted by Robert F.
Kennedy, Jr. and Florida-based attorney Mike Papantonio.

Seder also works as a periodic political contributor for MSNBC.

\section{2004 Republican National
Convention}\label{republican-national-convention}

\begin{itemize}
\item
  \emph{Shortly after Zell Miller gave his speech, Seder began searching
  (with a sign in hand) on the convention floor for a willing homosexual
  Republican to interview live on radio.}
\item
  \emph{On September 1, 2004, Seder was briefly detained by the United
  States Secret Service during his live, on-site coverage of the
  Republican National Convention at Madison Square Garden.}
\end{itemize}

On September 1, 2004, Seder was briefly detained by the United States
Secret Service during his live, on-site coverage of the Republican
National Convention at Madison Square Garden. Shortly after Zell Miller
gave his speech, Seder began searching (with a sign in hand) on the
convention floor for a willing homosexual Republican to interview live
on radio. Shortly thereafter, he was physically removed from the floor
and - after brief questioning - asked (or according to some,{[}who?{]}
"strongly encouraged") to leave the convention. Seder later commented
that his wearing of a lapel pin that he had been given by a Secret
Service agent at the Democratic National Convention earlier that year
had kept him from being ejected from the convention
completely.{[}citation needed{]}

\section{2017 MSNBC controversy}\label{msnbc-controversy}

\begin{itemize}
\item
  \emph{Seder responded that MSNBC was making a mistake and that,
  "there's no story here."}
\item
  \emph{On Sunday, December 3, 2017, Seder was notified by Jon Levine of
  TheWrap that they had been contacted by MSNBC who had decided to
  terminate Seder's contract and were about to break the story through
  their own publication.}
\end{itemize}

On November 28, 2017, American alt-right social media personality,
writer, and conspiracy theorist Mike Cernovich published a post on
Medium that resurfaced a deleted tweet Seder wrote in 2009 joking about
convicted statutory rapist and fugitive film director Roman Polanski.
The tweet read, "Don't care re Polanski, but I hope if my daughter is
ever raped it is by an older truly talented man w/ a great sense of mise
en scene." Cernovich insisted the tweet proved Seder tacitly endorsed
Polanski's sex crime. He then approached multiple journalists and news
outlets, including MSNBC, to break the story.

Seder found out about the brewing controversy the same evening en route
to a supermarket after being contacted by MSNBC Senior Vice President of
Communications Errol Cockfield Jr. asking him to explain the tweet.
Seder replied to Cockfield in an email explaining the point being made
in the tweet and the context in which he wrote it. Seder also provided
other tweets supporting his claim.

The next day, on November 29, 2017, Seder received a voicemail from
Cockfield indicating MSNBC's upper management was seriously considering
cutting ties with him. Seder responded that MSNBC was making a mistake
and that, "there's no story here." Seder further warned Cockfield that
if they moved forward with the termination, "You guys are going to be
the story." Seder also requested a formal termination email. Seder never
received the email, leading him to believe that this employment status
was still undecided.

On Sunday, December 3, 2017, Seder was notified by Jon Levine of TheWrap
that they had been contacted by MSNBC who had decided to terminate
Seder's contract and were about to break the story through their own
publication. Seder immediately sent Cockfield an inquiry regarding his
status. Cockfield, at first, did not have a status update but later
confirmed MSNBC was, in fact, dropping Seder.

\section{Firing}\label{firing}

\begin{itemize}
\item
  \emph{Further, Seder chided MSNBC's decision to terminate his
  employment concluding, "I think they're afraid of those people."}
\item
  \emph{By then, Seder noted that advertisers on The Majority Report
  with Sam Seder podcast were also being contacted and pressured by
  Cernovich and his team to cut ties with the show over the tweet.}
\end{itemize}

The next day, on December 4, 2017, TheWrap announced that MSNBC had
elected to sever ties with Seder by not renewing his contract (due to
expire in February 2018) due to the controversial tweet. Seder defended
the tweet by pointing out that, taken in context of the current events
around the time he posted it, it was a satiric response to a petition
urging Polanski's release from detention in Switzerland. That he was, in
fact, mocking Polanski's apologists. An anonymous MSNBC source defended
the termination, "It gives us pause when we see alt-right figures
whipping up attention about our action but the reality is Seder made a
rape joke." After news of the termination broke, Cernovich released a
Twitter video celebrating his triumph.

By then, Seder noted that advertisers on The Majority Report with Sam
Seder podcast were also being contacted and pressured by Cernovich and
his team to cut ties with the show over the tweet. In response, Seder
launched a GoFundMe campaign to help maintain funding for the show in
the face of potential loss of advertising revenue. In an episode of the
podcast titled, "I'm Under Attack By the Nazi Alt-Right", Seder said,
"this smear involves the willful misinterpretation of a tweet that I
posted in 2009" and that he will "never be ashamed of criticizing those
who would excuse the predation of women or girls."

Seder revealed plans to use a portion of the GoFundMe proceeds to
produce a three-minute video educating people on Cernovich's tactics. He
surmised Cernovich's ploy had been retribution for his frequent
criticism of US President Donald Trump as well as Republican Alabama
Senate candidate Roy Moore who was accused of sexual assault. Further,
Seder chided MSNBC's decision to terminate his employment concluding, "I
think they're afraid of those people."

The news of Seder's dismissal sparked an almost immediate backlash. Over
12,000 people signed a petition protesting Seder's termination, arguing
that Cernovich had acted in malice and was deliberately
mischaracterizing the tweet. AV Club wrote that "MSNBC has now fully
bought into that smear campaign ... whose openly stated goal is the
destruction of news outlets just like it through the use of blatantly
manipulative trolling techniques. Mother Jones rebuked MSNBC for
capitulating "to the demands of a lunatic conservative." HuffPost chided
that Cernovich was now MSNBC's new "De Facto Ombudsman." MSNBC primetime
anchor Chris Hayes tweeted, "The entire culture and our politics are now
dominated by people who have weaponized bad faith and shamelessness."
Hayes tweeted several times against the decision by his own network,
including: "Also, I reiterate my longstanding position that people
shouldn't be fired for a tweet, *particularly* one that is obviously
being read in manifestly bad faith." Actress and comedian Sarah
Silverman also tweeted in support of Seder.

\section{Rehiring}\label{rehiring}

\begin{itemize}
\item
  \emph{\\
  There was considerable dissent within MSNBC over Seder's termination.}
\item
  \emph{He also sarcastically tweeted that he was "thrilled" MSNBC
  offered Seder his job back while threatening to "bring Sam Seder's
  Tweet out every time the media goes after someone else for a Tweet."}
\item
  \emph{On December 7, 2017, MSNBC decided to reverse their decision to
  terminate Seder's employment.}
\end{itemize}

There was considerable dissent within MSNBC over Seder's termination.
Some employees expressed concerns that his firing would encourage other
far-right personalities to launch similar smear campaigns. A senior
MSNBC employee characterized the capitulation as "really weak" and
"pathetic". MSNBC's management itself was unsettled by the celebratory
reaction from the far-right. On December 7, 2017, MSNBC decided to
reverse their decision to terminate Seder's employment. MSNBC President
Phil Griffin said in a statement, "Sometimes you just get one wrong, and
that's what happened here. We made our initial decision for the right
reasons---because we don't consider rape to be a funny topic to be joked
about. But we've heard the feedback, and we understand the point Sam was
trying to make in that tweet was actually in line with our values, even
though the language was not. Sam will be welcome on our air going
forward." In response, Seder issued a statement while accepting his job
back:.mw-parser-output .templatequote\{overflow:hidden;margin:1em
0;padding:0 40px\}.mw-parser-output .templatequote
.templatequotecite\{line-height:1.5em;text-align:left;padding-left:1.6em;margin-top:0\}

Columbia Journalism Review cited the incident as an example of a broader
pattern of far-right media personalities using online smear campaigns to
get mainstream journalists fired. Cernovich, who also promoted the
Pizzagate conspiracy theory, insisted "date rape doesn't exist" and was
himself arrested for rape (though subsequently pleading guilty to
battery), acknowledged that "some are saying Seder was making a joke or
being sarcastic." However, he still insisted he didn't misrepresent the
tweet and that he simply "reported on what {[}Seder{]} said." He later
admitted that the whole incident was a stunt while claiming victory
explaining, retroactively, it was meant to bring attention to what he
perceived was a double standard and a lack of "diversity of viewpoint"
in the media. He also sarcastically tweeted that he was "thrilled" MSNBC
offered Seder his job back while threatening to "bring Sam Seder's Tweet
out every time the media goes after someone else for a Tweet." On
December 9, 2017, having failed to get Seder fired, Cernovich claimed
that his wife was being stalked at the behest of the media.

\section{2020 and 2022 elections}\label{and-2022-elections}

\begin{itemize}
\item
  \emph{Months after announcing his satirical candidacy, a poll by Third
  Party Watch among registered libertarian voters had Seder in first
  place, beating candidate Adam Kokesh by 9 points.}
\item
  \emph{In January 24, 2019, Seder announced his intention be a
  candidate in the Libertarian Party primary for the 2020 presidential
  election as a satirical candidate, due to his opposition to American
  libertarians.}
\end{itemize}

In January 24, 2019, Seder announced his intention be a candidate in the
Libertarian Party primary for the 2020 presidential election as a
satirical candidate, due to his opposition to American libertarians.

He subsequently announced his intention to challenge incumbent senator
Chuck Schumer for the Democratic Party nomination for the 2022 New York
Senate election.

Months after announcing his satirical candidacy, a poll by Third Party
Watch among registered libertarian voters had Seder in first place,
beating candidate Adam Kokesh by 9 points.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{On August 9, 2005, Seder's wife Nikki gave birth to a daughter,
  Myla Rae Seder.}
\item
  \emph{On April 27, 2018, Seder announced on his daily podcast, The
  Majority Report with Sam Seder, that he and his wife were separated.}
\end{itemize}

On August 9, 2005, Seder's wife Nikki gave birth to a daughter, Myla Rae
Seder.{[}citation needed{]} On March 7, 2013, the family gave birth to
their second child, a son named Saul Arthur Seder.

On April 27, 2018, Seder announced on his daily podcast, The Majority
Report with Sam Seder, that he and his wife were separated.{[}citation
needed{]}

\section{Filmography}\label{filmography}

\begin{itemize}
\item
  \emph{America Undercover TV actor (2005)}
\item
  \emph{The Show TV actor (1996)}
\end{itemize}

All American Girl TV actor (1994)

The Show TV actor (1996)

The Big Fall actor (1996)

Who's the Caboose? actor, director, co-writer, co-producer (1997)

Spin City TV actor (1997)

Next Stop Wonderland actor (1998)

Home Movies TV voiceover (1999)

Sex and the City TV actor (2000)

Happy Accidents actor (2000)

Endsville actor (2000)

Home Movies Voice of Fenton Mewley and other smaller roles (2001--2004)

Beat Cops actor, writer, producer (2001)

Saddle Rash TV voiceover (2002)

I'm with Busey director (2003)

Pilot Season TV actor, director, writer, producer (2004)

America Undercover TV actor (2005)

Jesus Camp cameo (2006)

Lucy, the Daughter of the Devil TV voiceover (2007)

Assy McGee TV voiceover \& writer (2008)

Bob's Burgers TV voiceover (2011--)

\section{References}\label{references}

\begin{itemize}
\item
  \emph{Scher, Bill; Garofalo, Janeane; Seder, Sam (2006), Wait!}
\item
  \emph{Seder, Sam; Sherrill, Stephen (2006), F.U.B.A.R.}
\end{itemize}

Notes

Footnotes

Bibliography

Seder, Sam; Sherrill, Stephen (2006), F.U.B.A.R.: America's Right-Wing
Nightmare, HarperCollins, ISBN~978-0-06-186364-6

Scher, Bill; Garofalo, Janeane; Seder, Sam (2006), Wait! Don't Move to
Canada: A Stay-and-Fight Strategy to Win Back America, Rodale,
ISBN~9781594863967

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Sam Seder, Bob Knight (December 12, 2005).}
\item
  \emph{Sam Seder on IMDb}
\end{itemize}

Official website

Sam Seder, Bob Knight (December 12, 2005). "War on the War on the War on
Christmas". CNN News (Transcript). CNN.

Sam Seder on IMDb
