\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Sara\%20Murray\%20\%28journalist\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Sara Murray (journalist)}\label{sara-murray-journalist}

\begin{itemize}
\item
  \emph{Sara Murray is an American journalist who works as political
  correspondent for CNN.}
\end{itemize}

Sara Murray is an American journalist who works as political
correspondent for CNN.

\section{Life and career}\label{life-and-career}

\begin{itemize}
\item
  \emph{Murray was born and raised in Mount Pleasant, Michigan and is a
  graduate of the University of Maryland.}
\item
  \emph{In 2015, she accepted a position with CNN where she covered the
  Republican candidates in the 2016 presidential campaign.}
\end{itemize}

Murray was born and raised in Mount Pleasant, Michigan and is a graduate
of the University of Maryland. After school, she moved to New York City
where she worked for the Wall Street Journal where she covered the 2008
financial crisis and Mitt Romney's 2012 presidential campaign; and later
served as their anchor for their digital network. In 2015, she accepted
a position with CNN where she covered the Republican candidates in the
2016 presidential campaign. Presently she focuses on the Russia
investigation of President Donald Trump.

\section{Personal life}\label{personal-life}

\begin{itemize}
\item
  \emph{Murray lives in Washington, D.C.}
\end{itemize}

In April 2017, she married MSNBC correspondent Garrett Haake in Austin,
Texas. Murray lives in Washington, D.C.

\section{References}\label{references}
