\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Sastur\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Sastur}\label{sastur}

\begin{itemize}
\item
  \emph{Sastur is a panchayat village in the state of Maharashtra,
  India.}
\item
  \emph{There is only the single village of Sastur in the Sastur gram
  panchayat.}
\item
  \emph{The village of Sastur is 20~km by road northwest of the village
  of Madaj and 22~km by road east of the village of Lohara Bk..}
\item
  \emph{Administratively, Sastur is under Lohara Tahsil of Osmanabad
  District in Maharashtra.}
\end{itemize}

Sastur is a panchayat village in the state of Maharashtra, India.
Administratively, Sastur is under Lohara Tahsil of Osmanabad District in
Maharashtra. There is only the single village of Sastur in the Sastur
gram panchayat. The village of Sastur is 20~km by road northwest of the
village of Madaj and 22~km by road east of the village of Lohara Bk..

\section{Demographics}\label{demographics}

\begin{itemize}
\item
  \emph{In the 2011 census, the village of Sastur had 7,259
  inhabitants.}
\end{itemize}

In the 2001 census, the village of Sastur had 6,612 inhabitants, with
3,386 males (51.2\%) and 3,226 females (48.8\%), for a gender ratio of
953 females per thousand males.

In the 2011 census, the village of Sastur had 7,259 inhabitants.

\section{Notes}\label{notes}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{"Official Website of Osmanabad District".}
\end{itemize}

"Official Website of Osmanabad District".
