\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Sweet\%20Hearts\%20Dance\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Sweet Hearts Dance}\label{sweet-hearts-dance}

\begin{itemize}
\item
  \emph{Sweet Hearts Dance is a 1988 American comedy drama film directed
  by Robert Greenwald.}
\end{itemize}

Sweet Hearts Dance is a 1988 American comedy drama film directed by
Robert Greenwald. The screenplay by Ernest Thompson centers on two small
town couples, one married for several years and the other at the
beginning of their relationship.

The film was shot on location in Hyde Park, Vermont at Becky and Brendy
Mullins' house. The school gym built as a film set remained in use as
Hyde Park Elementary School's gym until 2017.

\section{Plot}\label{plot}

\begin{itemize}
\item
  \emph{His best friend, local school board president Sam Manners, is on
  the verge of starting a relationship with Adie Nims, a recent
  transplant from Florida and the new teacher at the grade school.}
\item
  \emph{Using subsequent holidays as a background, the film focuses on
  both their efforts to recapture the magic of their early years
  together.}
\end{itemize}

It's Halloween, and New England contractor Wiley Boon, married to his
high school sweetheart Sandra and the father of three children, feels
smothered after fifteen years of the same routine and is facing a
midlife crisis. His best friend, local school board president Sam
Manners, is on the verge of starting a relationship with Adie Nims, a
recent transplant from Florida and the new teacher at the grade school.
During Thanksgiving dinner, Wiley and Sandra have a minor disagreement
that prompts him to leave his family and move into a mobile home to sort
through his feelings of emotional unrest. Using subsequent holidays as a
background, the film focuses on both their efforts to recapture the
magic of their early years together.

\section{Cast}\label{cast}

\begin{itemize}
\item
  \emph{Holly Marie Combs as Debs Boon}
\item
  \emph{Justin Henry as Kyle Boon}
\item
  \emph{Susan Sarandon as Sandra Boon}
\item
  \emph{Don Johnson as Wiley Boon}
\end{itemize}

Don Johnson as Wiley Boon

Susan Sarandon as Sandra Boon

Jeff Daniels as Sam Manners

Elizabeth Perkins as Adie Nims

Kate Reid as Pearne Manners

Justin Henry as Kyle Boon

Holly Marie Combs as Debs Boon

Bernie Sanders as Bernie, a man giving out Halloween candy

\section{Reception}\label{reception}

\section{Critical response}\label{critical-response}

\begin{itemize}
\item
  \emph{She added, "Sweet Hearts Dance .}
\end{itemize}

Janet Maslin of the New York Times thought "the rapport between the
film's four principals is so well established that its romantic
quadrille about the various ups and downs of two humorously contrasting
couples really does come to life." She added, "Sweet Hearts Dance . . .
approaches love as a series of fits and starts. It approaches narrative
in much the same way, which would be more of a problem if the film were
not so enjoyably loose-jointed anyhow . . . {[}It{]} tends to drift, but
it has good humor and an easygoing appeal, not to mention a thoroughly
attractive cast."

Roger Ebert of the Chicago Sun-Times rated the film two out of four
stars. He felt the screenplay "seems to meander in whatever direction
the filmmakers thought they could find an inspiration" but added, "And
yet the film is not without merit. All of the performances are
interesting, and although I was not surprised that three of the four
leads were good, I was surprised at how effective Don Johnson was in his
role. It's the best thing he's done, and shows he can do good things."
He concluded, "There were times when I thought I'd seen this movie
before -- maybe in The Four Seasons by Alan Alda or, for that matter, in
any film by Alda. Made by sensitive, sophisticated middle-age men about
sensitive middle-age men who are a little less sophisticated, the movie
drips with nostalgia, but sometimes what everybody seems to want isn't
love, but a gift certificate at L.L. Bean. The lifestyle itself
threatens to upstage the drama, and as the wholesome New Englanders go
about their wholesome New England pastimes, even suffering begins to
look picturesque."

Rita Kempley of the Washington Post described the film as
"thirtysomething in needlepoint" and commented, "With its comfortable
characters and small-town setting, it's as homey as hash -- almost as if
the director just threw it together like a housewife with unexpected
company. It's not a grand movie, but an enjoyable midlife comedy that
features Don Johnson in a breakthrough performance."

\section{Box office}\label{box-office}

\begin{itemize}
\item
  \emph{The film was not a box office success.}
\end{itemize}

The film was not a box office success.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Sweet Hearts Dance on IMDb}
\item
  \emph{Sweet Hearts Dance at AllMovie}
\item
  \emph{Sweet Hearts Dance at Rotten Tomatoes}
\end{itemize}

Sweet Hearts Dance on IMDb

Sweet Hearts Dance at Rotten Tomatoes

Sweet Hearts Dance at AllMovie
