\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/The\_Scarlet\_Letter\_\%28miniseries\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{The Scarlet Letter
(miniseries)}\label{the-scarlet-letter-miniseries}

\begin{itemize}
\item
  \emph{The Scarlet Letter is a 1979 miniseries based on the novel of
  the same name by Nathaniel Hawthorne: it aired on WGBH from March 3,
  1979 to March 24, 1979.}
\end{itemize}

The Scarlet Letter is a 1979 miniseries based on the novel of the same
name by Nathaniel Hawthorne: it aired on WGBH from March 3, 1979 to
March 24, 1979. The series is four episodes long, 60 minutes each. Part
2 won the 1979 Emmy Award for Outstanding Video Tape Editing for a
Limited Series or Special for film editors Ken Denisoff, Janet McFadden,
and Tucker Wiard.

In 1979, when most literary programs were being produced in the United
Kingdom, Boston public television station WGBH decided to produce a
homegrown literary classic of its own. The result was this version of
Hawthorne's enduring novel of Puritan America in search of its soul.
Hester Prynne becomes stigmatized after committing adultery, and is
doomed to live with the consequences forever. Hawthorne's themes, the
nature of sin, social hypocrisy, and community repression, still
reverberate through American society.

Hester Prynne (Meg Foster) is a young, Puritan woman who commits
adultery while her husband is in Europe, and, upon the birth of her
illegitimate child, is subsequently condemned to wear a scarlet "A" for
the rest of her life. Her secret partner, the Reverend Arthur
Dimmesdale, (John Heard) writhes in private torment as he deals with
hiding his sin. The person of Hester's husband, Roger Chillingworth
(Kevin Conway) completes this grim triangle as the mysterious situation
leads to a shattering climax. The story follows the main characters as
they grapple with sin, forgiveness, and redemption.

\section{Principal Cast}\label{principal-cast}

\begin{itemize}
\item
  \emph{Josef Sommer as Nathaniel Hawthorne}
\item
  \emph{Elisa Erali as Pearl Prynne}
\item
  \emph{Meg Foster as Hester Prynne}
\end{itemize}

Josef Sommer as Nathaniel Hawthorne

Meg Foster as Hester Prynne

Elisa Erali as Pearl Prynne

John Heard as Reverend Arthur Dimmesdale

Kevin Conway as Roger Chillingworth

George Martin as the Rev. Mr. Wilson

\section{Crew}\label{crew}

\begin{itemize}
\item
  \emph{Original music by John Morris}
\item
  \emph{Produced by Rick Hauser and Herbert Hirschman}
\item
  \emph{Writing credits: Nathaniel Hawthorne, Allan Knee, and Alvin
  Sapinsley}
\item
  \emph{Directed by Rick Hauser}
\end{itemize}

Directed by Rick Hauser

Writing credits: Nathaniel Hawthorne, Allan Knee, and Alvin Sapinsley

Produced by Rick Hauser and Herbert Hirschman

Original music by John Morris

Cinematography by Bob Collins

Film editing by Ken Denisoff, Janet McFadden, and Tucker Wiard

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{The Scarlet Letter on IMDb}
\end{itemize}

The Scarlet Letter on IMDb
