\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Timeline\%20of\%20the\%20Donald\%20Trump\%20presidency\%20\%282017\%20Q1\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Timeline of the Donald Trump presidency (2017
Q1)}\label{timeline-of-the-donald-trump-presidency-2017-q1}

\begin{itemize}
\item
  \emph{The following is a timeline of the presidency of Donald Trump
  during the first quarter of 2017.}
\end{itemize}

The following is a timeline of the presidency of Donald Trump during the
first quarter of 2017. To navigate between quarters, see Timeline of the
Donald Trump presidency.

\section{Overview}\label{overview}

\section{Economy and employment}\label{economy-and-employment}

\begin{itemize}
\item
  \emph{In the first quarter of 2017, the real US GDP increased at an
  annual rate of 0.7\%, the slowest growth since the first quarter of
  2014.}
\item
  \emph{On March 31, 2017, the U.S. national debt stood at \$19.8
  trillion representing a quarterly decline of 0.65\%.}
\end{itemize}

In the first quarter of 2017, the real US GDP increased at an annual
rate of 0.7\%, the slowest growth since the first quarter of 2014. The
growth was primarily caused by an increase in business structures and
equipment (such as mining and wells), industrial supplies and materials
(like petroleum), and services. This was offset by decreases in motor
vehicles and parts, private inventory investment, and government
spending. On March 31, 2017, the U.S. national debt stood at \$19.8
trillion representing a quarterly decline of 0.65\%.

\section{Public opinion}\label{public-opinion}

\begin{itemize}
\item
  \emph{According to FiveThirtyEight, President Trump's approval rate at
  the end of March was 40.5\%, down 5\% from the start of his
  presidency.}
\end{itemize}

According to FiveThirtyEight, President Trump's approval rate at the end
of March was 40.5\%, down 5\% from the start of his presidency.

\section{Timeline}\label{timeline}

\section{January 2017}\label{january-2017}

\section{Week 1}\label{week-1}

\section{Week 2}\label{week-2}

\section{February 2017}\label{february-2017}

\section{Week 2}\label{week-2-1}

\section{Week 3}\label{week-3}

\section{Week 4}\label{week-4}

\section{Week 5}\label{week-5}

\section{Week 6}\label{week-6}

\section{March 2017}\label{march-2017}

\section{Week 6}\label{week-6-1}

\section{Week 7}\label{week-7}

\section{Week 8}\label{week-8}

\section{Week 9}\label{week-9}

\section{Week 10}\label{week-10}

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Presidential transition of Donald Trump}
\item
  \emph{First 100 days of Donald Trump's presidency}
\item
  \emph{List of executive actions by Donald Trump}
\item
  \emph{List of presidential trips made by Donald Trump (international
  trips)}
\end{itemize}

Presidential transition of Donald Trump

First 100 days of Donald Trump's presidency

List of executive actions by Donald Trump

List of presidential trips made by Donald Trump (international trips)

Timeline of the 2016 United States presidential election

\section{References}\label{references}

\section{External links}\label{external-links}
