\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Tom\_Swift\_and\_His\_Airship\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Tom Swift and His Airship}\label{tom-swift-and-his-airship}

\begin{itemize}
\item
  \emph{Tom Swift and His Airship, or, The Stirring Cruise of the Red
  Cloud, is Volume 3 in the original Tom Swift novel series published by
  Grosset \& Dunlap.}
\end{itemize}

Tom Swift and His Airship, or, The Stirring Cruise of the Red Cloud, is
Volume 3 in the original Tom Swift novel series published by Grosset \&
Dunlap.

\section{Plot summary}\label{plot-summary}

\begin{itemize}
\item
  \emph{No sooner is Tom in the air than he is blamed for the robbery.}
\item
  \emph{In Tom Swift and His Airship, Tom Swift has finished his latest
  invention- the Red Cloud, a fast and innovative airship.}
\end{itemize}

In Tom Swift and His Airship, Tom Swift has finished his latest
invention- the Red Cloud, a fast and innovative airship. Tom is anxious
for a cross-country trial, but just before he and his friends take off,
the Shopton bank is robbed. No sooner is Tom in the air than he is
blamed for the robbery. Suddenly, he's a wanted fugitive but doesn't
know why until he's halfway across the country. With no safe harbor or
friend on the land below, Tom must race back to Shopton to clear his
name before he's shot out of the sky.

\section{Inventions \& innovation}\label{inventions-innovation}

\begin{itemize}
\item
  \emph{It was fast, achieving over 80~mph if pressed, and could stay in
  the air for two weeks at a time, if Tom wanted.}
\item
  \emph{Barton Swift, Tom's father, is nearing completion of a submarine
  design that promises to be the most advanced in the world.}
\item
  \emph{Tom Swift, and his friend (John Sharp - aeronaut
  extraordinaire), designed and built the Red Cloud: an airship that was
  half blimp/dirigible and half airplane.}
\end{itemize}

Tom Swift, and his friend (John Sharp - aeronaut extraordinaire),
designed and built the Red Cloud: an airship that was half
blimp/dirigible and half airplane. In fact, it had two wings (like the
World War I biplanes) extending out from a spacious gondola which sat
beneath the rather voluminous gas-filled balloon. It was fast, achieving
over 80~mph if pressed, and could stay in the air for two weeks at a
time, if Tom wanted. Perhaps the most fantastic element of the craft was
the gondola, which was luxuriously appointed with multiple rooms; e.g.,
a kitchen, an engine room, and a first-rate observation room from which
Tom would steer the ship, while looking out the surrounding windows.

Barton Swift, Tom's father, is nearing completion of a submarine design
that promises to be the most advanced in the world.

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Tom Swift and his Airship public domain audiobook at LibriVox}
\end{itemize}

Tom Swift and his Airship public domain audiobook at LibriVox
