\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Trump\%20National\%20Golf\%20Club\%20\%28Bedminster\%2C\%20New\%20Jersey\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Trump National Golf Club (Bedminster, New
Jersey)}\label{trump-national-golf-club-bedminster-new-jersey}

\begin{itemize}
\item
  \emph{Approximately 40 miles (64~km) west of New York City in Somerset
  County, it is owned and operated by The Trump Organization.}
\item
  \emph{Trump National Golf Club is a private golf club located on
  Lamington Road in Bedminster, New Jersey.}
\end{itemize}

Trump National Golf Club is a private golf club located on Lamington
Road in Bedminster, New Jersey. Approximately 40 miles (64~km) west of
New York City in Somerset County, it is owned and operated by The Trump
Organization.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{The club hosted the wedding of Trump's daughter, Ivanka Trump,
  in October 2009.}
\item
  \emph{The director of the New Jersey chapter of the Sierra Club said
  that Trump was "hiding behind a farmland assessment to get a massive
  tax break on a golf course."}
\item
  \emph{For tax purposes, The Trump Organization secured a
  classification of the Bedminster course and the Trump course in Colts
  Neck as farmland.}
\end{itemize}

Donald Trump bought the 520-acre property, which included the estate of
automaker John Z. De Lorean, for less than \$35 million in 2002. It was
previously known as Lamington Farm and the site of a foundering golf
course construction project. The 36-hole club was designed by golf
course architects Tom Fazio and Tom Fazio II. The first course opened
fifteen years ago in 2004.

Membership in the club costs at the most \$300,000 In 2005, Golf
Magazine ranked it at \#73 in the United States and \#84 by Golf Digest
for 2005 and 2006.

For tax purposes, The Trump Organization secured a classification of the
Bedminster course and the Trump course in Colts Neck as farmland. For
that purpose, part of the acreage at Bedminster is used for growing hay
and raising eight goats. The Wall Street Journal estimated that the use
of the property tax exemption for farmland reduced the tax bill on the
two golf courses from \$80,000 to less than \$1,000. The director of the
New Jersey chapter of the Sierra Club said that Trump was "hiding behind
a farmland assessment to get a massive tax break on a golf course."

The club hosted the wedding of Trump's daughter, Ivanka Trump, in
October 2009.

\section{Majors host}\label{majors-host}

\begin{itemize}
\item
  \emph{The golf club hosted the U.S. Women's Open from July 13--16,
  2017.}
\end{itemize}

The golf club hosted the U.S. Women's Open from July 13--16, 2017. The
Professional Golfers' Association of America awarded the course the 2022
Men's PGA Championship.

\section{Trump presidency}\label{trump-presidency}

\begin{itemize}
\item
  \emph{In November 2016, after Trump's presidential election, the
  property was used to host meetings for the Donald Trump presidential
  transition.}
\item
  \emph{In 2017 it became one of the three official presidential
  residencies, the other two being Trump Tower in New York and
  Mar-a-Lago in Florida.}
\item
  \emph{Trump stated that staying at his property in Bedminster is less
  expensive and disruptive than going to Trump Tower in New York.}
\end{itemize}

In November 2016, after Trump's presidential election, the property was
used to host meetings for the Donald Trump presidential transition.
Representative Leonard Lance predicted that the resort could become
"Camp David North". In 2017 it became one of the three official
presidential residencies, the other two being Trump Tower in New York
and Mar-a-Lago in Florida.

In May 2017, Trump started to use the property for weekend retreats
during the summer when Mar-a-Lago is closed for the season. Trump stated
that staying at his property in Bedminster is less expensive and
disruptive than going to Trump Tower in New York. This made the property
the "Summer White House". It is usually used from May to September.

In August 2017, the estate was used as a working vacation of the
President for a duration of 17 days while the White House underwent
renovations approved by the Obama administration and overseen by the
Trump administration.

In August 2018, the estate became again the site of the President's
working vacation for close to two weeks.

White House staffers receive the same discounts (15--70\%) as club
members at the Club's pro shop, an arrangement that was flagged as
"absolutely wrong" by the Citizens for Responsibility and Ethics in
Washington.

\section{Security issues}\label{security-issues}

\begin{itemize}
\item
  \emph{Due to security concerns, flight restrictions are imposed by the
  Federal Aviation Administration within a 30-mile radius during Trump's
  stays at his golf club.}
\item
  \emph{With the official designation as an official residence of Trump,
  Congress appropriated up to \$41 million for its security costs in the
  time between inauguration and October 1, 2017.}
\end{itemize}

Due to security concerns, flight restrictions are imposed by the Federal
Aviation Administration within a 30-mile radius during Trump's stays at
his golf club. Restrictions affect 19 airports in New Jersey and
Pennsylvania, among them two airports that have to close down completely
because they are within a 10 mile-radius, namely Solberg Airport in
Readington, New Jersey and Somerset Airport in Bedminster, New
Jersey.Additionally, Academy of Model Aviation Clubs cannot fly model
airplanes in this same 30-mile radius.

With the official designation as an official residence of Trump,
Congress appropriated up to \$41 million for its security costs in the
time between inauguration and October 1, 2017.

\section{Trump Mausoleum}\label{trump-mausoleum}

\begin{itemize}
\item
  \emph{Trump indicated that he wants to be buried at the Bedminster
  golf course.}
\item
  \emph{In 2015, Trump received the approval to build a family cemetery
  at the estate that would include a classical mausoleum.}
\end{itemize}

In 2015, Trump received the approval to build a family cemetery at the
estate that would include a classical mausoleum. Trump indicated that he
wants to be buried at the Bedminster golf course.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Donald Trump and golf}
\item
  \emph{List of things named after Donald Trump}
\end{itemize}

Donald Trump and golf

List of things named after Donald Trump

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Official website}
\end{itemize}

Official website
