\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/University\_of\_Sanya\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{University of Sanya}\label{university-of-sanya}

\begin{itemize}
\item
  \emph{University of Sanya was ranked the 2nd in private universities
  in China in 2018, according to Chinese university ranking (CUAA).}
\item
  \emph{It currently has made partnerships with State Forestry and
  Grassland Administration of China, Department of Culture Radio
  Television Publication and Sports of Hainan, Hainan Provincial Tourism
  Bureau, Peking University, Tsinghua University, Institute of Deep-sea
  Science and Engineering of Chinese Academy of Sciences, Hainan
  Microsoft Innovation Center, etc.}
\end{itemize}

University of Sanya (Chinese: 三亚学院, commonly referred to as USY) was
established in 2005 and endowed by Zhejiang Geely Holding Group as one
of the first privately owned universities in China. Based in Sanya along
the coast of the South China Sea, the university offers one of the best
cultural experiences in China. It currently consists of 18 schools and
an office of academic affairs. 71 undergraduate degree programs in 9
categories are offered, including law, literature, economics,
management, engineering, science, agriculture, education, and art. In
2018, the university enrolled 20,000 students together with 1000
teaching and research staff members. University of Sanya was ranked the
2nd in private universities in China in 2018, according to Chinese
university ranking (CUAA).

The university offers courses across geographical regions, and made a
global footprint for its innovative teaching and research. It currently
has made partnerships with State Forestry and Grassland Administration
of China, Department of Culture Radio Television Publication and Sports
of Hainan, Hainan Provincial Tourism Bureau, Peking University, Tsinghua
University, Institute of Deep-sea Science and Engineering of Chinese
Academy of Sciences, Hainan Microsoft Innovation Center, etc. USY
pioneers in several key subjects, such as Tourism Management, Financial
Engineering, in which Saxo Fintech Business school was established
jointly with Saxo Bank, and Automotive Engineering with Geely Auto.
Thanks to its geographical location in Sanya which is boasted as
"China's Hawaii", many academic forums including Global Humboldt Forum
were held on campus. Boao Forum for Asia also has a proximity to the
university and city.

\section{Partner Institution}\label{partner-institution}

\section{Malaysia}\label{malaysia}

\begin{itemize}
\item
  \emph{Universiti Tunku Abdul Rahman}
\end{itemize}

Universiti Tunku Abdul Rahman

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{List of universities and colleges in Hainan}
\end{itemize}

List of universities and colleges in Hainan

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Official website}
\end{itemize}

Official website
