\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/United\%20States\%20Senate\%20election\%20in\%20Vermont\%2C\%202018\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{2018 United States Senate election in
Vermont}\label{united-states-senate-election-in-vermont}

\begin{itemize}
\item
  \emph{Incumbent independent Senator Bernie Sanders was re-elected to a
  third term.}
\item
  \emph{The 2018 United States Senate election in Vermont was held
  November 6, 2018, alongside a gubernatorial election, U.S. House
  election, and other state and local elections.}
\end{itemize}

The 2018 United States Senate election in Vermont was held November 6,
2018, alongside a gubernatorial election, U.S. House election, and other
state and local elections. Incumbent independent Senator Bernie Sanders
was re-elected to a third term. The primaries were held on August 14.

\section{Background}\label{background}

\begin{itemize}
\item
  \emph{Two-term independent Senator Bernie Sanders was reelected with
  71\% of the vote in 2012.}
\item
  \emph{After losing, he announced that he would return to the Senate as
  an independent, and later stated that he would run for reelection as
  an independent in 2018.}
\item
  \emph{Sanders ran for the 2016 Democratic presidential nomination.}
\item
  \emph{He will be 77 years old in 2018.}
\end{itemize}

Two-term independent Senator Bernie Sanders was reelected with 71\% of
the vote in 2012. Sanders, a former candidate for president in the 2016
election and one of two independent members of Congress, is a
self-described democratic socialist.

Sanders has caucused with the Democratic Party since taking office in
2007, and he is the Ranking Member of the Budget Committee. He will be
77 years old in 2018. Sanders ran for the 2016 Democratic presidential
nomination. After losing, he announced that he would return to the
Senate as an independent, and later stated that he would run for
reelection as an independent in 2018.

\section{Independents}\label{independents}

\section{Candidates}\label{candidates}

\begin{itemize}
\item
  \emph{Bernie Sanders, incumbent U.S.}
\end{itemize}

Brad Peacock, farmer

Bernie Sanders, incumbent U.S. Senator (caucuses with Democrats)

\section{Endorsements}\label{endorsements}

\section{Democratic primary}\label{democratic-primary}

\section{Candidates}\label{candidates-1}

\section{Nominee}\label{nominee}

\begin{itemize}
\item
  \emph{Bernie Sanders, incumbent U.S.}
\end{itemize}

Bernie Sanders, incumbent U.S. Senator (declined nomination)

\section{Eliminated in primary}\label{eliminated-in-primary}

\begin{itemize}
\item
  \emph{Folasade Adeluola, activist}
\end{itemize}

Folasade Adeluola, activist

\section{Not on ballot}\label{not-on-ballot}

\begin{itemize}
\item
  \emph{Jon Svitavsky, homelessness activist}
\end{itemize}

Jon Svitavsky, homelessness activist

\section{Withdrawn}\label{withdrawn}

\begin{itemize}
\item
  \emph{Al Giordano, journalist}
\end{itemize}

Al Giordano, journalist

\section{Results}\label{results}

\section{Republican primary}\label{republican-primary}

\section{Candidates}\label{candidates-2}

\section{Nominee}\label{nominee-1}

\begin{itemize}
\item
  \emph{Lawrence Zupan, real estate broker (nominated by party)}
\end{itemize}

Lawrence Zupan, real estate broker (nominated by party)

\section{Withdrew nomination}\label{withdrew-nomination}

\begin{itemize}
\item
  \emph{H. Brooke Paige, former CEO of Remmington News Service}
\end{itemize}

H. Brooke Paige, former CEO of Remmington News Service

\section{Eliminated in primary}\label{eliminated-in-primary-1}

\begin{itemize}
\item
  \emph{Lawrence Zupan, real estate agent}
\item
  \emph{Rocky De La Fuente, businessman}
\item
  \emph{Jasdeep Pannu, attorney}
\end{itemize}

Rocky De La Fuente, businessman

Jasdeep Pannu, attorney

Lawrence Zupan, real estate agent

\section{Did not file}\label{did-not-file}

\begin{itemize}
\item
  \emph{Scott Milne, businessman, nominee for Governor in 2014 and
  nominee for the U.S. Senate in 2016}
\item
  \emph{John MacGovern, former Massachusetts State Representative and
  nominee for the U.S. Senate in 2012}
\end{itemize}

John MacGovern, former Massachusetts State Representative and nominee
for the U.S. Senate in 2012

Scott Milne, businessman, nominee for Governor in 2014 and nominee for
the U.S. Senate in 2016

\section{Results}\label{results-1}

\section{Post-primary}\label{post-primary}

\begin{itemize}
\item
  \emph{The Vermont Republican Party picked Lawrence Zupan, who came in
  2nd place in the primary, to be the Republican nominee.}
\item
  \emph{H. Brooke Paige, who also won the Republican nominations for
  U.S. House, state Attorney General, state Secretary of State, state
  Treasurer and state Auditor, withdrew from all but the Secretary of
  State race on August 24 in order to allow the Vermont Republican Party
  to name replacement candidates.}
\end{itemize}

H. Brooke Paige, who also won the Republican nominations for U.S. House,
state Attorney General, state Secretary of State, state Treasurer and
state Auditor, withdrew from all but the Secretary of State race on
August 24 in order to allow the Vermont Republican Party to name
replacement candidates. The Vermont Republican Party picked Lawrence
Zupan, who came in 2nd place in the primary, to be the Republican
nominee.

\section{General election}\label{general-election}

\section{Predictions}\label{predictions}

\begin{itemize}
\item
  \emph{*Highest rating given}
\end{itemize}

*Highest rating given

\section{Polling}\label{polling}

\section{Results}\label{results-2}

\begin{itemize}
\item
  \emph{Sanders won re-election with 67.3\% of the vote against eight
  other candidates.}
\end{itemize}

Sanders won re-election with 67.3\% of the vote against eight other
candidates.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Vermont gubernatorial election, 2018}
\item
  \emph{United States Senate elections, 2018}
\end{itemize}

United States Senate elections, 2018

Vermont gubernatorial election, 2018

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Russell Beste (I) for Senate}
\item
  \emph{Bernie Sanders (I) for Senate}
\item
  \emph{Jon Svitavsky (I) for Senate}
\item
  \emph{Brad Peacock (I) for Senate}
\end{itemize}

Candidates at Vote Smart

Candidates at Ballotpedia

Campaign finance at FEC

Campaign finance at Center for Responsive Politics

Official campaign websites

Russell Beste (I) for Senate

Edward Gilbert Jr. (I) for Senate

Reid Kane (LUP) for Senate

Brad Peacock (I) for Senate

Bernie Sanders (I) for Senate

Jon Svitavsky (I) for Senate

Lawrence Zupan (R) for Senate
