\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/Washington\_Street\_\%28Indianapolis\%29\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Washington Street
(Indianapolis)}\label{washington-street-indianapolis}

\begin{itemize}
\item
  \emph{The street follows the route of the National Road for almost all
  of its length in the city of Indianapolis.}
\item
  \emph{Washington Street is the primary east--west street in
  Indianapolis, in the central part of the U.S. state of Indiana.}
\item
  \emph{The street delineates north--south address numbering for the
  eastern two-thirds of the city; Rockville Road separates north and
  south from the western border of the city until it meets Washington
  Street in Wayne Township at Tibbs Avenue.}
\end{itemize}

Washington Street is the primary east--west street in Indianapolis, in
the central part of the U.S. state of Indiana. The street follows the
route of the National Road for almost all of its length in the city of
Indianapolis. For a time, its entire length was designated as U.S.
Route~40 (US~40) before that highway was re-aligned with the southern
segment of Interstate~465 (I-465); now only the segments of Washington
Street between I-465 and the city limits on either side of the city are
part of US~40.

The street delineates north--south address numbering for the eastern
two-thirds of the city; Rockville Road separates north and south from
the western border of the city until it meets Washington Street in Wayne
Township at Tibbs Avenue.

\section{Route description}\label{route-description}

\begin{itemize}
\item
  \emph{After merging with Rockville Road, Washington Street heads more
  directly east toward downtown Indianapolis.}
\item
  \emph{The street travels south of the Washington Square Mall as it
  approaches Cumberland, Indiana, where it terminates at Carroll Road.}
\item
  \emph{Washington Street begins in the west at the intersection with
  Raceway Road.}
\item
  \emph{On the far east side of the city, US~40 again joins Washington
  Street at the interchange with I-465.}
\end{itemize}

Washington Street begins in the west at the intersection with Raceway
Road. As it heads east-northeast, it passes by the Indianapolis
International Airport, which lies to south. Immediately thereafter, it
has an interchange with I-465 on the west side of the city, where US~40
diverges. After merging with Rockville Road, Washington Street heads
more directly east toward downtown Indianapolis. Approaching downtown it
passes the Indiana Medical History Museum on the former site of Central
State Hospital for the Insane; it then passes the headquarters of the
Indianapolis Public Transportation Corporation, which is in buildings
that once housed the Duesenberg Automobile and Motors Company.

On the west side of downtown, Washington Street passes by the
Indianapolis Zoo and White River Gardens, crosses the White River, and
traverses White River State Park, with the Indiana State Museum and
Eiteljorg Museum of American Indians and Western Art on the north side
of the street and Victory Field on the south. Within downtown, the
street carries only westbound traffic; eastbound traffic is routed a
block south to Maryland Street where it passes by the Indiana Convention
Center. Among the buildings directly on Washington Street within the
central business district are (from west to east): the Indiana
Statehouse; the Indiana Theatre, home of the Indiana Repertory Theatre;
the headquarters of the Simon Property Group; the Circle Centre shopping
mall; the Barnes and Thornburg Building (which until the 1960s was the
tallest building in the city); and the City-County Building. Washington
also runs under the Indianapolis Artsgarden, a suspended glass structure
at the intersection with Illinois Street. Washington does not intersect
Monument Circle (the city's town square); rather, the Circle is located
on Market Street, one block north of the intersection of Washington with
Meridian Street.

On the eastern edge of downtown, Washington Street has an interchange
with the I-65/I-70 "Inner Loop". As it continues east, it travels
through or by the Cole-Noble and Rural-Sherman neighborhoods. In the
Irvington Historic District, an early suburb of Indianapolis, Washington
crosses Pleasant Run Creek with its associated parkway and trail. On the
far east side of the city, US~40 again joins Washington Street at the
interchange with I-465. The street travels south of the Washington
Square Mall as it approaches Cumberland, Indiana, where it terminates at
Carroll Road.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Indianapolis portal}
\item
  \emph{Indiana portal}
\end{itemize}

U.S. Roads portal

Indiana portal

Indianapolis portal

\section{References}\label{references}
