\textbf{From Wikipedia, the free encyclopedia}

https://en.wikipedia.org/wiki/\%C5\%8Cuchi-juku\\
Licensed under CC BY-SA 3.0:\\
https://en.wikipedia.org/wiki/Wikipedia:Text\_of\_Creative\_Commons\_Attribution-ShareAlike\_3.0\_Unported\_License

\section{Ōuchi-juku}\label{ux14duchi-juku}

\begin{itemize}
\item
  \emph{Ōuchi-juku (大内宿, Ōuchi-juku) was a small post station in
  Japan's Edo period and part of the Aizu Nishi Kaidō.}
\item
  \emph{It is now located in the town of Shimogō in Minamiaizu District,
  Fukushima Prefecture, and is famous for the numerous traditional
  thatched buildings from the Edo Period that line its main street.}
\end{itemize}

Ōuchi-juku (大内宿, Ōuchi-juku) was a small post station in Japan's Edo
period and part of the Aizu Nishi Kaidō. It is now located in the town
of Shimogō in Minamiaizu District, Fukushima Prefecture, and is famous
for the numerous traditional thatched buildings from the Edo Period that
line its main street.

\section{History}\label{history}

\begin{itemize}
\item
  \emph{Many buildings have been preserved as they were before the Meiji
  Restoration, and the area has been designated as an Important
  Preservation District for Groups of Traditional Buildings.}
\item
  \emph{Ōuchi-juku was an important post town whose buildings served as
  shops, inns and restaurants for travellers.}
\end{itemize}

Ōuchi-juku was an important post town whose buildings served as shops,
inns and restaurants for travellers. Many buildings have been preserved
as they were before the Meiji Restoration, and the area has been
designated as an Important Preservation District for Groups of
Traditional Buildings. The village is now a popular tourist attraction.

\section{See also}\label{see-also}

\begin{itemize}
\item
  \emph{Groups of Traditional Buildings}
\end{itemize}

Simogo,Fukushima

Groups of Traditional Buildings

To-no-hetsuri

\section{Gallery}\label{gallery}

\begin{itemize}
\item
  \emph{Beautiful bird's eye view of Ouchi-juku.}
\end{itemize}

Beautiful bird's eye view of Ouchi-juku.

\section{References}\label{references}

\section{External links}\label{external-links}

\begin{itemize}
\item
  \emph{Ouchi-juku(Travel association)}
\end{itemize}

Ouchi-juku(Travel association)
